### 2015-12-31 paper.tex
Initial Commit

%% bare_conf_compsoc.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE Computer
%% Society conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[conference,compsoc]{IEEEtran}
% Some/most Computer Society conferences require the compsoc mode option,
% but others may want the standard conference format.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference,compsoc]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/pkg/ifpdf
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.
%
% Note that some packages require special options to format as the Computer
% Society requires. In particular, Computer Society  papers do not use
% compressed citation ranges as is done in typical IEEE papers
% (e.g., [1]-[4]). Instead, they list every citation separately in order
% (e.g., [1], [2], [3], [4]). To get the latter we need to load the cite
% package with the nocompress option which is supported by cite.sty v4.0
% and later.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/pkg/graphicx
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/pkg/epslatex
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics.
%
% Note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/amsmath

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/pkg/algorithms
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/pkg/algorithmicx

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/array

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a sans serif font rather
% than the serif font used in traditional IEEE formatting and thus the need
% to invoke different subfig.sty package options depending on whether
% compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/pkg/subfig

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure.
% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
% corrections already built into the system in which case a warning will
% be issued if an attempt is made to load fixltx2e.sty as it is no longer
% needed.
% The latest version and documentation can be found at:
% http://www.ctan.org/pkg/fixltx2e

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/pkg/stfloats
% Do not use the stfloats baselinefloat ability as the IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that the IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/pkg/dblfloatfix

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/pkg/url
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls for\\ IEEE Computer Society Conferences}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Michael Shell}
\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
Georgia Institute of Technology\\
Atlanta, Georgia 30332--0250\\
Email: http://www.michaelshell.org/contact.html}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678-2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page (and note that there is less available width in this regard for
% compsoc conferences compared to traditional conferences), use this
% alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE Computer Society conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\ifCLASSOPTIONcompsoc
  % The Computer Society usually uses the plural form
  \section*{Acknowledgments}
\else
  % regular IEEE prefers the singular form
  \section*{Acknowledgment}
\fi

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

%\begin{thebibliography}{1}

%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

%\end{thebibliography}

\bibliography{paper}

% that's all folks
\end{document}

### 2016-01-06 paper.tex
Formulas, Figures, etc.

@@
-%% bare_conf_compsoc.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE Computer
-%% Society conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-\documentclass[conference,compsoc]{IEEEtran}
+\documentclass[conference]{IEEEtran}
 % Some/most Computer Society conferences require the compsoc mode option,
 % but others may want the standard conference format.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference,compsoc]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
 
@@
 
+\usepackage[pdftex]{graphicx}
+\graphicspath{{./png/}}
+\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+
 % *** GRAPHICS RELATED PACKAGES ***
@@
 % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+%\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
 \else
@@
 % *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
+\usepackage{amsmath}
+\interdisplaylinepenalty=2500
 
@@
 % 
-%\usepackage{algorithmic}
+% \usepackage{algorithmic}
 % algorithmic.sty was written by Peter Williams and Rogerio Brito.
@@
 % 
-%\usepackage{array}
+% \usepackage{array}
 % Frank Mittelbach's and David Carlisle's array.sty patches and improves
@@
 
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=footnotesize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a sans serif font rather
-% than the serif font used in traditional IEEE formatting and thus the need
-% to invoke different subfig.sty package options depending on whether
-% compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
 \hyphenation{op-tical net-works semi-conduc-tor}
@@
 \begin{document}
-%
-% paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
-\title{Bare Demo of IEEEtran.cls for\\ IEEE Computer Society Conferences}
+\title{A Proposal for an Intuitionistic Fuzzy Inference System}
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{\IEEEauthorblockN{Michael Shell}
-\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-Georgia Institute of Technology\\
-Atlanta, Georgia 30332--0250\\
-Email: http://www.michaelshell.org/contact.html}
-\and
-\IEEEauthorblockN{Homer Simpson}
-\IEEEauthorblockA{Twentieth Century Fox\\
-Springfield, USA\\
-Email: homer@thesimpsons.com}
-\and
-\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-\IEEEauthorblockA{Starfleet Academy\\
-San Francisco, California 96678-2391\\
-Telephone: (800) 555--1212\\
-Fax: (888) 555--1212}}
+\author{\IEEEauthorblockN{Amaury Hernandez-Aguila, Mario
+    Garcia-Valdez, Oscar Castillo}
+  \IEEEauthorblockA{Tijuana Institute of Technology\\
+    Division of Graduate Studies and Graduates\\
+    Tijuana, Mexico\\
+    Email: \{amherag,mario,ocastillo\}@tectijuana.edu.mx}}
 
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page (and note that there is less available width in this regard for
-% compsoc conferences compared to traditional conferences), use this
-% alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
 \maketitle
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract
 \begin{abstract}
-The abstract goes here.
+
 \end{abstract}
 
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
 \IEEEpeerreviewmaketitle
@@
 \section{Introduction}
-% no \IEEEPARstart
-This demo file is intended to serve as a ``starter file''
-for IEEE Computer Society conference papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8b and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
 
-\hfill mds
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Aenean egestas semper leo sed accumsan.
+Donec id est quis nibh blandit semper quis sed nisl.
+Mauris bibendum dapibus mi posuere egestas.
+In at lectus elementum, mollis arcu eget, feugiat enim.
+Vivamus viverra in lorem nec rhoncus.
+Curabitur venenatis, nisi sed hendrerit maximus, libero quam aliquam nunc, quis pulvinar ipsum enim a lacus.
+Sed dapibus hendrerit leo.
+Sed porttitor imperdiet dui, a pulvinar ante accumsan in.
+Proin vel nulla enim.
+Praesent sagittis eget mauris ornare suscipit.
+Sed vehicula suscipit accumsan.
+Integer tortor libero, lacinia ac maximus id, sagittis at enim.
+Mauris vitae est elit.
 
-\hfill August 26, 2015
+Nulla ac tortor ipsum.
+Suspendisse vel diam sapien.
+Mauris ac lobortis eros.
+Etiam mollis magna nec sapien egestas, nec tincidunt elit tempus.
+Nulla ullamcorper rutrum odio, vitae vehicula justo semper non.
+Nunc bibendum enim elit, et auctor nisi vulputate ut.
+Donec nulla risus, dapibus vel mi id, sagittis rhoncus quam.
+Suspendisse facilisis tortor ac tortor posuere facilisis.
+Proin dignissim mollis blandit.
+Donec suscipit tortor at elit blandit vestibulum.
+Praesent leo ante, vehicula vitae commodo id, porttitor et erat.
+Quisque nisl eros, finibus non sem sed, egestas dapibus diam.
+Cras et maximus tortor.
+Vivamus rhoncus et sem non tempus.
+Nulla nec velit nec magna rhoncus finibus.
 
-\subsection{Subsection Heading Here}
-Subsection text here.
+Maecenas varius ipsum et eros efficitur, quis iaculis lacus placerat.
+Morbi nibh metus, lobortis ut nunc tempor, cursus dignissim odio.
+Duis elementum leo lorem, maximus hendrerit risus bibendum ac.
+Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
+Curabitur consequat tincidunt orci et gravida.
+Curabitur non vehicula ipsum, ut accumsan magna.
+Nullam vel accumsan tellus.
+Quisque tortor metus, blandit eget varius id, laoreet nec ipsum.
+Mauris molestie quam vel mattis aliquam.
+Donec aliquet iaculis ipsum, nec feugiat nibh facilisis at.
+Nunc velit leo, commodo tristique feugiat non, rutrum eget felis.
+Proin a pellentesque nisi, ac facilisis ex.
+Praesent in fermentum dolor, nec commodo lorem.
+Ut gravida nisl gravida dapibus faucibus.
+Vivamus cursus faucibus ipsum a suscipit.
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+Aenean eu ultrices diam.
+Phasellus vel facilisis neque, vitae convallis metus.
+Donec nec mauris a lorem ullamcorper fermentum.
+Donec ac lacus consectetur, maximus nibh quis, rhoncus dui.
+Donec vestibulum tortor tellus, vel porta ligula pharetra sit amet.
+Duis in massa id dolor tempus mattis.
+Integer in molestie odio, ac placerat nulla.
+Ut non erat in lectus tempor interdum.
+Quisque et porttitor erat.
+Morbi ligula metus, vehicula sit amet est vitae, sodales tristique magna.
+Aenean consequat massa ipsum, at porttitor sapien eleifend et.
+Donec vestibulum suscipit nibh, sed ultrices elit pharetra et.
+Suspendisse nulla dui, volutpat sed accumsan vitae, tincidunt nec nisl.
+Aenean et justo et nisl volutpat condimentum vitae a lorem.
+
+Nam commodo lacus eu arcu facilisis, et hendrerit urna ullamcorper.
+Nunc mollis magna ante, sit amet ullamcorper velit porta quis.
+Fusce risus sem, varius ac ornare et, tristique sit amet ligula.
+Nullam egestas mi odio, vitae maximus purus suscipit vitae.
+Vivamus eget consequat neque.
+Mauris iaculis condimentum arcu, ac facilisis lorem.
+Maecenas dignissim eu ipsum nec convallis.
+
+\section{Related Work}
+
+Aenean eu ultrices diam.
+Phasellus vel facilisis neque, vitae convallis metus.
+Donec nec mauris a lorem ullamcorper fermentum.
+Donec ac lacus consectetur, maximus nibh quis, rhoncus dui.
+Donec vestibulum tortor tellus, vel porta ligula pharetra sit amet.
+Duis in massa id dolor tempus mattis.
+Integer in molestie odio, ac placerat nulla.
+Ut non erat in lectus tempor interdum.
+Quisque et porttitor erat.
+Morbi ligula metus, vehicula sit amet est vitae, sodales tristique magna.
+Aenean consequat massa ipsum, at porttitor sapien eleifend et.
+Donec vestibulum suscipit nibh, sed ultrices elit pharetra et.
+Suspendisse nulla dui, volutpat sed accumsan vitae, tincidunt nec nisl.
+Aenean et justo et nisl volutpat condimentum vitae a lorem.
+
+Nam commodo lacus eu arcu facilisis, et hendrerit urna ullamcorper.
+Nunc mollis magna ante, sit amet ullamcorper velit porta quis.
+Fusce risus sem, varius ac ornare et, tristique sit amet ligula.
+Nullam egestas mi odio, vitae maximus purus suscipit vitae.
+Vivamus eget consequat neque.
+Mauris iaculis condimentum arcu, ac facilisis lorem.
+Maecenas dignissim eu ipsum nec convallis.
+
+\section{Preliminaries}
+
+% intuitionistic fuzzy set
+\begin{equation}
+  A^{*} = \{\langle x, \mu _{A} (x), \nu _{A} (x) \rangle | x \in E\}
+\end{equation}
+
+% intuitionistic interval
+\begin{equation}
+  0 \leq \mu_{A}(x) + \nu_{A}(x) \leq 1
+\end{equation}
+
+% every ordinary fuzzy set has the form
+\begin{equation}
+  \{ \langle x, \mu_{A}(x), 1 - \mu_{A}(x) \rangle | x \in E \}
+\end{equation}
+
+% if
+\begin{equation}
+  \pi_{A}(x) = 1 - \mu_{A}(x) - \nu_{A}(x)
+\end{equation}
+
+\section{Proposed Method}
+
+\begin{enumerate}
+  \item if $t_{0}$ is $A_{1}$ then $p_{t+1}$ is $C_{1}$
+  \item if $t_{-6}$ is $A_{2}$ then $p_{t+1}$ is $C_{2}$
+  \item if $t_{-12}$ is $A_{3}$ then $p_{t+1}$ is $C_{3}$
+  \item if $t_{-18}$ is $A_{4}$ then $p_{t+1}$ is $C_{4}$
+\end{enumerate}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{fs-as-ifs}
+  \caption{Classic Fuzzy Set Represented as an Intuitionistic Fuzzy Set}
+  \label{fs-as-ifs}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{ifs}
+  \caption{An Example of an Intuitionistic Fuzzy Set}
+  \label{ifs}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{if-membership}
+  \caption{Comparison of $\mu(x)$ Against $i\mu(x)$}
+  \label{if-membership}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{if-membership-drastic}
+  \caption{Comparison of $\mu(x)$ Against $i\mu(x)$ With More Indeterminism}
+  \label{if-membership-drastic}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{if-coa-vs-coa}
+  \caption{Comparison of $CoA(A_{i})$ Against $iCoA{A_{i}}$}
+  \label{if-coa-vs-coa}
+\end{figure}
+
+% i-membership
+\begin{equation}
+  i\mu_{A}(x) = (\nu_{A}(x) + \mu_{A}(x))\mu_{A}(x)
+\end{equation}
+
+% CoA
+\begin{equation}
+  A_{CoA} = \dfrac{\sum_{i=1}^{N} \mu(x_{i})
+    x_{i}}{\sum_{i=1}^{N} \mu(x_{i})}
+\end{equation}
+
+%iCoA
+\begin{equation}
+  A_{iCoA} = \dfrac{\sum_{i=1}^{N} (\mu(x_{i}) + \nu(x_{i})) \mu(x_{i})
+    x_{i}}{\sum_{i=1}^{N} (\mu(x_{i}) + \nu(x_{i})) \mu(x_{i})}
+\end{equation}
+
+\begin{equation}
+  A_{iCoA} = \dfrac{\sum_{i=1}^{N} i\mu_{A}(x) x_{i}}{\sum_{i=1}^{N}
+    i\mu_{A}(x)}
+\end{equation}
+
+\section{Experiments}
+
+% \begin{figure}[!t]
+%   \centering
+%   \includegraphics[width=2.5in]{myfigure}
+%   where an .eps filename suffix will be assumed under latex, 
+%   and a .pdf suffix will be assumed for pdflatex; or what has been declared
+%   via \DeclareGraphicsExtensions.
+%   \caption{Simulation results for the network.}
+%   \label{fig_sim}
+% \end{figure}
+
+\section{Results}
+
+\begin{table}[!t]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Hypothesis Tests for the Training Stage}
+  \label{hypothesis-tests-training}
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value\\
+    \hline
+    T1 iFIS & 89.50 & 25.36 & 60 & \\
+    \hline
+    T1 FIS & 108.05 & 23.47 & 60 & -4.1584 \\
+    \hline
+    IT2 FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 \\
+    \hline
+    IT2 FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 \\
+    \hline
+  \end{tabular}
+\end{table}
+
+\begin{table}[!t]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Hypothesis Tests for the Testing Stage}
+  \label{hypothesis-tests}
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value\\
+    \hline
+    T1-iFIS & 160.99 & 65.70 & 60 & \\
+    \hline
+    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 \\
+    \hline
+    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 \\
+    \hline
+    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 \\
+    \hline
+  \end{tabular}
+\end{table}
 
@@
 % 
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
+% \begin{figure}[!t]
+%   \centering
+%   \includegraphics[width=2.5in]{myfigure}
 %   where an .eps filename suffix will be assumed under latex, 
@@
 %   via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
+%   \caption{Simulation results for the network.}
+%   \label{fig_sim}
+% \end{figure}
 
@@
 % 
-%\begin{table}[!t]
+% \begin{table}[!t]
 %%   increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
+%   \renewcommand{\arraystretch}{1.3}
 %   if using array.sty, it might be a good idea to tweak the value of
 %   \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
+%   \caption{An Example of a Table}
+%   \label{table_example}
+%   \centering
 
 \section{Conclusion}
-The conclusion goes here.
 
-% conference papers do not normally have an appendix
+\section{Future Work}
 
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
+\section{Throwing References}
 
-The authors would like to thank...
+\cite{atanassov1986intuitionistic}
+\cite{atanassov2003intuitionistic}
+\cite{davarzani2013novel}
+\cite{despi2013generalised}
+\cite{sharma2011cut}
+\cite{sharma2011cutgroups}
+\cite{akram2014intuitionistic}
+\cite{cornelis2001compositional}
+\cite{castillo2007intuitionistic}
+\cite{bustince1995method}
+\cite{marinov2005method}
+\cite{atanassov2013intuitionistic}
+\cite{zadeh1965fuzzy}
+\cite{klir1995fuzzy}
+\cite{pedrycz1998shadowed}
+\cite{mendel2001uncertain}
+\cite{mendel2002type}
+\cite{liang2000interval}
+\cite{mendel2006interval}
+\cite{karnik2001centroid}
+\cite{castro2007interval}
+\cite{wagner2013juzzy}
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%\end{thebibliography}
-
+\bibliographystyle{IEEEtran}
 \bibliography{paper}
 
-% that's all folks
 \end{document}

### 2016-01-06 paper.tex

@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Aenean egestas semper leo sed accumsan.
-Donec id est quis nibh blandit semper quis sed nisl.
-Mauris bibendum dapibus mi posuere egestas.
-In at lectus elementum, mollis arcu eget, feugiat enim.
-Vivamus viverra in lorem nec rhoncus.
-Curabitur venenatis, nisi sed hendrerit maximus, libero quam aliquam nunc, quis pulvinar ipsum enim a lacus.
-Sed dapibus hendrerit leo.
-Sed porttitor imperdiet dui, a pulvinar ante accumsan in.
-Proin vel nulla enim.
-Praesent sagittis eget mauris ornare suscipit.
-Sed vehicula suscipit accumsan.
-Integer tortor libero, lacinia ac maximus id, sagittis at enim.
-Mauris vitae est elit.
-
-Nulla ac tortor ipsum.
-Suspendisse vel diam sapien.
-Mauris ac lobortis eros.
-Etiam mollis magna nec sapien egestas, nec tincidunt elit tempus.
-Nulla ullamcorper rutrum odio, vitae vehicula justo semper non.
-Nunc bibendum enim elit, et auctor nisi vulputate ut.
-Donec nulla risus, dapibus vel mi id, sagittis rhoncus quam.
-Suspendisse facilisis tortor ac tortor posuere facilisis.
-Proin dignissim mollis blandit.
-Donec suscipit tortor at elit blandit vestibulum.
-Praesent leo ante, vehicula vitae commodo id, porttitor et erat.
-Quisque nisl eros, finibus non sem sed, egestas dapibus diam.
-Cras et maximus tortor.
-Vivamus rhoncus et sem non tempus.
-Nulla nec velit nec magna rhoncus finibus.
-
-Maecenas varius ipsum et eros efficitur, quis iaculis lacus placerat.
-Morbi nibh metus, lobortis ut nunc tempor, cursus dignissim odio.
-Duis elementum leo lorem, maximus hendrerit risus bibendum ac.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-Curabitur consequat tincidunt orci et gravida.
-Curabitur non vehicula ipsum, ut accumsan magna.
-Nullam vel accumsan tellus.
-Quisque tortor metus, blandit eget varius id, laoreet nec ipsum.
-Mauris molestie quam vel mattis aliquam.
-Donec aliquet iaculis ipsum, nec feugiat nibh facilisis at.
-Nunc velit leo, commodo tristique feugiat non, rutrum eget felis.
-Proin a pellentesque nisi, ac facilisis ex.
-Praesent in fermentum dolor, nec commodo lorem.
-Ut gravida nisl gravida dapibus faucibus.
-Vivamus cursus faucibus ipsum a suscipit.
-
-Aenean eu ultrices diam.
-Phasellus vel facilisis neque, vitae convallis metus.
-Donec nec mauris a lorem ullamcorper fermentum.
-Donec ac lacus consectetur, maximus nibh quis, rhoncus dui.
-Donec vestibulum tortor tellus, vel porta ligula pharetra sit amet.
-Duis in massa id dolor tempus mattis.
-Integer in molestie odio, ac placerat nulla.
-Ut non erat in lectus tempor interdum.
-Quisque et porttitor erat.
-Morbi ligula metus, vehicula sit amet est vitae, sodales tristique magna.
-Aenean consequat massa ipsum, at porttitor sapien eleifend et.
-Donec vestibulum suscipit nibh, sed ultrices elit pharetra et.
-Suspendisse nulla dui, volutpat sed accumsan vitae, tincidunt nec nisl.
-Aenean et justo et nisl volutpat condimentum vitae a lorem.
-
-Nam commodo lacus eu arcu facilisis, et hendrerit urna ullamcorper.
-Nunc mollis magna ante, sit amet ullamcorper velit porta quis.
-Fusce risus sem, varius ac ornare et, tristique sit amet ligula.
-Nullam egestas mi odio, vitae maximus purus suscipit vitae.
-Vivamus eget consequat neque.
-Mauris iaculis condimentum arcu, ac facilisis lorem.
-Maecenas dignissim eu ipsum nec convallis.
-
 \section{Related Work}
-
-Aenean eu ultrices diam.
-Phasellus vel facilisis neque, vitae convallis metus.
-Donec nec mauris a lorem ullamcorper fermentum.
-Donec ac lacus consectetur, maximus nibh quis, rhoncus dui.
-Donec vestibulum tortor tellus, vel porta ligula pharetra sit amet.
-Duis in massa id dolor tempus mattis.
-Integer in molestie odio, ac placerat nulla.
-Ut non erat in lectus tempor interdum.
-Quisque et porttitor erat.
-Morbi ligula metus, vehicula sit amet est vitae, sodales tristique magna.
-Aenean consequat massa ipsum, at porttitor sapien eleifend et.
-Donec vestibulum suscipit nibh, sed ultrices elit pharetra et.
-Suspendisse nulla dui, volutpat sed accumsan vitae, tincidunt nec nisl.
-Aenean et justo et nisl volutpat condimentum vitae a lorem.
-
-Nam commodo lacus eu arcu facilisis, et hendrerit urna ullamcorper.
-Nunc mollis magna ante, sit amet ullamcorper velit porta quis.
-Fusce risus sem, varius ac ornare et, tristique sit amet ligula.
-Nullam egestas mi odio, vitae maximus purus suscipit vitae.
-Vivamus eget consequat neque.
-Mauris iaculis condimentum arcu, ac facilisis lorem.
-Maecenas dignissim eu ipsum nec convallis.
 

### 2016-01-06 paper.tex
Adding results CSVs and structure

@@
 
+What is a fuzzy set? \cite{zadeh1965fuzzy}
+
+What is fuzzy logic? \cite{klir1995fuzzy}
+
+Types of fuzzy sets. Mendel book \cite{mendel2001uncertain}
+
+What is a fuzzy inference system?
+
+There can be different types. Type-2 \cite{mendel2002type}, interval
+t2 \cite{liang2000interval} and \cite{mendel2006interval}
+
+Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}
+
+What is a intuitionistic fuzzy set? \cite{atanassov1986intuitionistic}
+\cite{atanassov2003intuitionistic} \cite {despi2013generalised}
+
 \section{Related Work}
 
+Application of intuitionistic fuzzy sets, bacillus colonies
+recognition \cite{davarzani2013novel}
+
+Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}
+
+intuitionistic inference engine \cite{cornelis2001compositional}
+
+implementation of a ifis, castillo \cite{castillo2007intuitionistic}
+
+more inference \cite{bustince1995method}
+
+centroid of a type-2 fuzzy-set \cite{karnik2001centroid}
+
+and even more inference \cite{marinov2005method}
+
+Intuitionistic control washing machines \cite{akram2014intuitionistic}
+
 \section{Preliminaries}
+
+Define in more detail intuitionistic fuzzy sets.
+
+Formulas and basic explanation (below) \cite{atanassov2013intuitionistic}
 
@@
 
-\begin{enumerate}
-  \item if $t_{0}$ is $A_{1}$ then $p_{t+1}$ is $C_{1}$
-  \item if $t_{-6}$ is $A_{2}$ then $p_{t+1}$ is $C_{2}$
-  \item if $t_{-12}$ is $A_{3}$ then $p_{t+1}$ is $C_{3}$
-  \item if $t_{-18}$ is $A_{4}$ then $p_{t+1}$ is $C_{4}$
-\end{enumerate}
+How a classic fuzzy set is represented as a ifs. How an intuitionistic
+fuzzy set is represented in this work.
+
+How the non-membership is going to affect the membership (show
+formula). Present both examples (stating the parameters).
+
+How the coa is calculated (show formula and plot). How the formula can
+be contracted.
 
@@
 
+%iCoA contracted
 \begin{equation}
@@
 
-% \begin{figure}[!t]
-%   \centering
-%   \includegraphics[width=2.5in]{myfigure}
-%   where an .eps filename suffix will be assumed under latex, 
-%   and a .pdf suffix will be assumed for pdflatex; or what has been declared
-%   via \DeclareGraphicsExtensions.
-%   \caption{Simulation results for the network.}
-%   \label{fig_sim}
-% \end{figure}
+Comparisons against juzzy \cite{wagner2013juzzy}
+
+Compare using Mackey-Glass, 100 training, 50 for testing, because it
+took too much time. Genetic algorithm. Present parameters: mean 0-100,
+sd 30-70, mf 1, nmf 0.8-1.0.
+
+The rule base.
+
+\begin{enumerate}
+  \item if $t_{0}$ is $A_{1}$ then $p_{t+1}$ is $C_{1}$
+  \item if $t_{-6}$ is $A_{2}$ then $p_{t+1}$ is $C_{2}$
+  \item if $t_{-12}$ is $A_{3}$ then $p_{t+1}$ is $C_{3}$
+  \item if $t_{-18}$ is $A_{4}$ then $p_{t+1}$ is $C_{4}$
+\end{enumerate}
 
 \section{Results}
+
+Results can be found on https://github.com/amherag/wcci-2016-a
 
@@
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-% 
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-% 
-% \begin{figure}[!t]
-%   \centering
-%   \includegraphics[width=2.5in]{myfigure}
-%   where an .eps filename suffix will be assumed under latex, 
-%   and a .pdf suffix will be assumed for pdflatex; or what has been declared
-%   via \DeclareGraphicsExtensions.
-%   \caption{Simulation results for the network.}
-%   \label{fig_sim}
-% \end{figure}
+\section{Conclusion}
 
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-% 
-% \begin{table}[!t]
-%%   increase table row spacing, adjust to taste
-%   \renewcommand{\arraystretch}{1.3}
-%   if using array.sty, it might be a good idea to tweak the value of
-%   \extrarowheight as needed to properly center the text within the cells
-%   \caption{An Example of a Table}
-%   \label{table_example}
-%   \centering
-
-\section{Conclusion}
+This work mainly focuses on proving that the design is viable, but it
+also proves that at least in some cases the intuitionistic fis can
+out-perform the t1 and t2.
 
@@
 
-\section{Throwing References}
-
-\cite{atanassov1986intuitionistic}
-\cite{atanassov2003intuitionistic}
-\cite{davarzani2013novel}
-\cite{despi2013generalised}
-\cite{sharma2011cut}
-\cite{sharma2011cutgroups}
-\cite{akram2014intuitionistic}
-\cite{cornelis2001compositional}
-\cite{castillo2007intuitionistic}
-\cite{bustince1995method}
-\cite{marinov2005method}
-\cite{atanassov2013intuitionistic}
-\cite{zadeh1965fuzzy}
-\cite{klir1995fuzzy}
-\cite{pedrycz1998shadowed}
-\cite{mendel2001uncertain}
-\cite{mendel2002type}
-\cite{liang2000interval}
-\cite{mendel2006interval}
-\cite{karnik2001centroid}
-\cite{castro2007interval}
-\cite{wagner2013juzzy}
+We want to create a toolbox such as \cite{castro2007interval}
+We want to experiment with other data sets.
+We want to speed up the algorithm.
+We want to experiment with generalized type-2.
 

### 2016-01-06 paper.tex
starting Propose Method section

@@
 \begin{equation}
+  \label{intuitionistic-interval}
   0 \leq \mu_{A}(x) + \nu_{A}(x) \leq 1
@@
 \begin{equation}
+  \label{ifs-form}
   \{ \langle x, \mu_{A}(x), 1 - \mu_{A}(x) \rangle | x \in E \}
@@
 \begin{equation}
+  \label{fs-as-ifs-if}
   \pi_{A}(x) = 1 - \mu_{A}(x) - \nu_{A}(x)
@@
 
-How a classic fuzzy set is represented as a ifs. How an intuitionistic
-fuzzy set is represented in this work.
+The method, for now, consists on the procedures and elements
+necessary to construct a basic Intuitionistic Fuzzy Inference System
+(IFIS). This design was completed in order to make comparisons against
+classic fuzzy inference systems, such as Type-1 FIS, Interval
+Type-2 and General Type-2 FIS, and prove that
+the design was viable and able to contribute to better results than
+the classic FISs.
 
-How the non-membership is going to affect the membership (show
-formula). Present both examples (stating the parameters).
+In many works, intuitionistic fuzzy sets (IFSs) are constructed by
+hand, by interviewing experts who assign memberships and
+non-memberships to each of the values of a set (such as in
+\cite{davarzani2013novel}). This work proposes a convenient way of
+creating an IFS, imitating many systems that use Gaussian
+membership functions to facilitate an expert the representation of a
+fuzzy interpretation. An example of an IFS is depicted in
+Fig. \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
+satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
+the membership function as the red line, and the non-membership
+function as the blue line. In order to contruct the non-membership
+function, one has to invert a normal Gaussian membership function.
 
-How the coa is calculated (show formula and plot). How the formula can
-be contracted.
+Two convenient ways of modifying the non-membership function and
+satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
+the mean and the standard deviation of the Gaussian functions to be
+the same, and only vary the $height$ of the non-membership function,
+as is depicted in \ref{ifs}; and 2) one can set different means and
+standard deviations of the Gaussian membership and non-membership
+functions, but the $height$ of the membership function must be equal
+to $h_{mf} = 1 - h_{nmf}$, as this ensures that
+(\ref{intuitionistic-interval}) is satisfied. To clarify, the $height$
+of the membership function ($h_{mf}$) of an IFS is equal to
+$max(\mu(x))$, and the $height$ of the non-membership function
+($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.
+
+%\ref{ifs-diff-mu-sd}
+
+% How a classic fuzzy set is represented as a ifs. How an intuitionistic
+% fuzzy set is represented in this work.
+
+% How the non-membership is going to affect the membership (show
+% formula). Present both examples (stating the parameters).
+
+% How the coa is calculated (show formula and plot). How the formula can
+% be contracted.
 
@@
   \includegraphics[width=2.5in]{ifs}
-  \caption{An Example of an Intuitionistic Fuzzy Set}
+  \caption{An Example of an Intuitionistic Fuzzy Set - Same Mean and SD}
   \label{ifs}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{ifs-diff-mu-sd}
+  \caption{An Example of an Intuitionistic Fuzzy Set - Different Mean
+    and SD}
+  \label{ifs-diff-mu-sd}
 \end{figure}

### 2016-01-06 paper.tex
Adding more figures

@@
 \usepackage[pdftex]{graphicx}
-\graphicspath{{./png/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\graphicspath{{./png/}{./eps/}}
+\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
 
@@
 to $h_{mf} = 1 - h_{nmf}$, as this ensures that
-(\ref{intuitionistic-interval}) is satisfied. To clarify, the $height$
+(\ref{intuitionistic-interval}) is satisfied. An example of the latter
+case is shown in Fig. \ref{ifs-diff-mu-sd}.To clarify, the $height$
 of the membership function ($h_{mf}$) of an IFS is equal to
@@
 
-%\ref{ifs-diff-mu-sd}
+The first step
 
@@
 % be contracted.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[height=2.5in]{proposed-method-flow-chart}
+  \caption{Proposed Method Flow Chart}
+  \label{flow-chart}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{alpha-cut}
+  \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
+  \label{alpha-cut}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{ifs-union}
+  \caption{Union of Three $\alpha$-cut Intuitionistic Fuzzy Sets}
+  \label{ifs-union}
+\end{figure}
 

### 2016-01-06 paper.tex
2/3 of the proposed method done

--- 2016-01-06 paper.tex
@@
 
-How a classic fuzzy set is represented as a ifs. How an intuitionistic
-fuzzy set is represented in this work.
+The method, for now, consists on the procedures and elements
+necessary to construct a basic Intuitionistic Fuzzy Inference System
+(IFIS). This design was completed in order to make comparisons against
+classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
+Type-2 and General Type-2 FIS, and prove that
+the design was viable and able to contribute to better results than
+the classic FISs.
 
-How the non-membership is going to affect the membership (show
-formula). Present both examples (stating the parameters).
-
-How the coa is calculated (show formula and plot). How the formula can
-be contracted.
+In many works, intuitionistic fuzzy sets (IFSs) are constructed by
+hand, by interviewing experts who assign memberships and
+non-memberships to each of the values of a set (such as in
+\cite{davarzani2013novel}). This work proposes a convenient way of
+creating an IFS, imitating many systems that use Gaussian
+membership functions (MFs) to facilitate an expert the representation of a
+fuzzy interpretation. An example of an IFS is depicted in
+Fig. \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
+satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
+the MF as the red line, and the non-membership
+function (NMF) as the blue line. In order to contruct the NMF, one has
+to rotate a normal Gaussian MF by 180˚, and this can be seen as the
+complement of the fuzzy set corresponding to a Gaussian MF.
 
@@
 
+Two convenient ways of modifying the NMF and
+satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
+the mean and the standard deviation of the Gaussian functions to be
+the same, and only vary the $height$ of the NMF,
+as is depicted in Fig. \ref{ifs}; and 2) one can set different means and
+standard deviations of the Gaussian membership and non-membership
+functions, but the $height$ of the MF must be equal
+to $h_{mf} = 1 - h_{nmf}$, as this ensures that
+(\ref{intuitionistic-interval}) is satisfied. An example of the latter
+case is shown in Fig. \ref{ifs-diff-mu-sd}. To clarify, the $height$
+of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
+$height$ of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.
+
 \begin{figure}[!t]
@@
   \includegraphics[width=2.5in]{ifs}
-  \caption{An Example of an Intuitionistic Fuzzy Set}
+  \caption{An Example of an Intuitionistic Fuzzy Set - Same Mean and SD}
   \label{ifs}
 \end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{ifs-diff-mu-sd}
+  \caption{An Example of an Intuitionistic Fuzzy Set - Different Mean
+    and SD}
+  \label{ifs-diff-mu-sd}
+\end{figure}
+
+The first step in an inference process in a classic FIS (a flow chart
+for the process in an IFIS is given in Fig. \ref{flow-chart}) is to
+determine what membership corresponds to a given input, given a set of
+MFs. This is straightforward in a classic FIS, as the
+membership to each input is already established in the membership
+fuzzy set. For an IFIS, this work proposes a method to determine a
+membership given a MF and a NMF,
+which is described in (\ref{imembership}), and receives the name of
+$i\mu$ (intuitionistic membership).
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[height=2.5in]{proposed-method-flow-chart}
+  \caption{Proposed Method Flow Chart}
+  \label{flow-chart}
+\end{figure}
+
+% i-membership
+\begin{equation}
+  \label{imembership}
+  i\mu_{A}(x) = (\nu_{A}(x) + \mu_{A}(x))\mu_{A}(x)
+\end{equation}
+
+A comparison of a MF (red line) against an intuitionistic
+membership function (blueline) is shown in Fig.
+\ref{if-membership}. The parameters for both the MF and NMF are $\mu =
+50$ and $SD = 15$, but the $height$ for the NMF is set at $0.5$. This
+results in an intuitionistic MF that appears to have the same mean,
+but a smaller standard deviation. A more elaborated example is shown
+in Fig. \ref{if-membership-drastic}, where the parameters of the MF
+are $\mu = 50$, $SD = 15$ and $h = 0.8$, and the parameters of the NMF
+are $\mu = 30$, $SD = 20$ and $h = 0.2$. As can be noted, the
+indeterminancy ($\pi$) is high in this example, which results in a
+smaller $SD$ for the intuitionistic MF. Moreover, the difference in
+means and standard deviations generates a change of the mean for the
+intuitionistic MF.
 
@@
 
+The next step in the inference process is to perform an $\alpha$-cut
+on the associated consequents to the antecedents that are activated by
+the inputs. In a classic FIS, this process is straightforward, as the
+memeberships in a fuzzy set representing a consequent are ``cut'' by
+following (\ref{alpha-cut}) for every element in a fuzzy set
+representing a consequent. In an intuitionistic MF, one can follow
+the same procedure in order to obtain the $\alpha$-cut in the MF part,
+but to obtain the $\alpha$-cut in the NMF, (\ref{nmf-alpha-cut}) must
+be followed. In (\ref{nmf-alpha-cut}), the counterintuitive part is
+that one has to find the corresponding $\nu$ for a given $\mu_{alpha}$.
+
+\begin{equation}
+  \label{alpha-cut}
+  \alpha(\mu (x),\mu_{\alpha}) =
+  \begin{cases}
+    \mu (x), & \text{if}\ \mu (x) \leq \mu_{alpha}  \\
+    \mu_{\alpha}, & \text{otherwise}
+  \end{cases}
+\end{equation}
+
+\begin{equation}
+  \label{nmf-alpha-cut}
+  \alpha_{NMF}(\nu (x),\mu_{\alpha}) =
+  \begin{cases}
+    \nu (x), & \text{if}\ \nu (x) \geq \nu (\mu_{alpha})  \\
+    \nu (\mu_{alpha}), & \text{otherwise}
+  \end{cases}
+\end{equation}
+
+% How the coa is calculated (show formula and plot). How the formula can
+% be contracted.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{alpha-cut}
+  \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
+  \label{alpha-cut}
+\end{figure}
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{ifs-union}
+  \caption{Union of Three $\alpha$-cut Intuitionistic Fuzzy Sets}
+  \label{ifs-union}
+\end{figure}
+
 \begin{figure}[!t]
@@
 \end{figure}
-
-% i-membership
-\begin{equation}
-  i\mu_{A}(x) = (\nu_{A}(x) + \mu_{A}(x))\mu_{A}(x)
-\end{equation}
 

### 2016-01-06 paper.tex

@@
 be followed. In (\ref{nmf-alpha-cut}), the counterintuitive part is
-that one has to find the corresponding $\nu$ for a given $\mu_{alpha}$.
+that one has to find the corresponding $\nu$ for a given
+$\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} =
+0.6$, is depicted in Fig. \ref{alpha-cut-example}.
 
@@
 
-% How the coa is calculated (show formula and plot). How the formula can
-% be contracted.
-
 \begin{figure}[!t]
@@
   \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
-  \label{alpha-cut}
+  \label{alpha-cut-example}
 \end{figure}
+
+After performing every necessary $\alpha$-cut, one has to apply the
+union operator over every resulting fuzzy set, in order to aggregate
+the weights of all the consequents. The union operator is defined by
+K. Atanassov \cite{atanassov2013intuitionistic}, for every two IFSs A
+and B, as in (\ref{union-operator}). An example of an union of three
+IFSs is shown in Fig. (\ref{ifs-union}).
+
+\begin{equation}
+  \label{union-operator}
+  \begin{aligned}
+    A \cup B  = &\{ \langle x, max(\mu_{A} (x), \mu_{B} (x)),\\
+    &\quad min(\nu_{A} (x), \nu_{B} (x)) \rangle | x \in E \}
+\end{aligned}
+\end{equation}
 
@@
 
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=2.5in]{if-coa-vs-coa}
-  \caption{Comparison of $CoA(A_{i})$ Against $iCoA{A_{i}}$}
-  \label{if-coa-vs-coa}
-\end{figure}
+Finally, one has to defuzzify the aggregation of the $\alpha$-cut
+consequents, in order to obtain a crisp number that represents
+it. There are a number of methods that can be used to defuzzify a
+fuzzy set, but the most frequently found in the literature is the
+Center of Area (CoA), or simply centroid. One can obtain the centroid
+of a classic fuzzy set A by using (\ref{center-of-area}). For an
+IFS, one can use the concept of intuitionistic membership ($i\mu$) and
+extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
+substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
+(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).
 
@@
 \begin{equation}
+  \label{center-of-area}
   A_{CoA} = \dfrac{\sum_{i=1}^{N} \mu(x_{i})
@@
 \begin{equation}
+  \label{if-coa}
   A_{iCoA} = \dfrac{\sum_{i=1}^{N} (\mu(x_{i}) + \nu(x_{i})) \mu(x_{i})
@@
 \begin{equation}
+  \label{if-coa-simplified}
   A_{iCoA} = \dfrac{\sum_{i=1}^{N} i\mu_{A}(x) x_{i}}{\sum_{i=1}^{N}
@@
 \end{equation}
+
+Fig. \ref{if-coa-vs-coa} shows the plot of the defuzzification of
+several IFSs with $CoA$ (red line) and $iCoA$ (blue line), with means set
+from 0 to 100 for the MF, and -20 to 80 for the NMF, and standard
+deviations of 15 for the MF, and 20 for the NMF.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=2.5in]{if-coa-vs-coa}
+  \caption{Comparison of $CoA_{A_{i}}$ Against $iCoA_{A_{i}}$}
+  \label{if-coa-vs-coa}
+\end{figure}
 

### 2016-01-08 paper.tex

@@
 are $\mu = 30$, $SD = 20$ and $h = 0.2$. As can be noted, the
-indeterminancy ($\pi$) is high in this example, which results in a
+indeterminacy ($\pi$) is high in this example, which results in a
 smaller $SD$ for the intuitionistic MF. Moreover, the difference in
@@
 
-Comparisons against juzzy \cite{wagner2013juzzy}
+The purpose of the experiments in this work is to demonstrate that the
+proposed method is viable for performing inference using
+intuitionistic fuzzy sets instead of classic fuzzy sets, i.e., that
+the concepts of intuitionistic membership ($i\mu$) and intuitionistic
+center of area ($iCoA$) enable an extension to traditional fuzzy
+inference systems to support indeterminacy and non-membership. To
+demonstrate this claim, this work presents a series of experiments
+where the proposed method is compared against Type-1 Fuzzy Inference
+Systems (T1-FISs) and Interval Type-2 Fuzzy Inference Systems
+(T2-FISs) with uncertain mean and uncertain standard deviation.
 
-Compare using Mackey-Glass, 100 training, 50 for testing, because it
-took too much time. Genetic algorithm. Present parameters: mean 0-100,
-sd 30-70, mf 1, nmf 0.8-1.0.
+The initial (and ambitious) hypothesis is that a Type-1 Intuitionistic Fuzzy System (T1-IFIS)
+should perform better than a T1-FIS, as it can handle both uncertainty
+and indeterminacy, and it is unclear if an IFIS should perform better
+than a T2-FIS. The experiments presented in this work
+cannot prove this statement profoundly, as the results will only test for a
+single situation, which is the prediction of a subset of the
+Mackey-Glass time series.
 
-The rule base.
+% Comparisons against juzzy \cite{wagner2013juzzy}
+
+% Compare using Mackey-Glass, 100 training, 50 for testing, because it
+% took too much time. Genetic algorithm. Present parameters: mean 0-100,
+% sd 30-70, mf 1, nmf 0.8-1.0.
+
+% The rule base.
 

### 2016-01-08 paper.tex
First comments
In Spanish for now :)

@@
 
+%Empieza aquí 
 There can be different types. Type-2 \cite{mendel2002type}, interval
@@
 
+%o incluso aquí
 Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}
@@
 
+% (Mario): 
+% Más que definir los elementos, mejor justificar el motivo de la propuesta
+% al parecer es por que Type-2 is time-consuming  
+% Esto si:
+% What is a intuitionistic fuzzy set 
+% Y después justificar, debido a esto, proponemos un FIS intucionista
+% Después lo clasico de como esta dividido el trabajo
 \section{Related Work}
@@
 
-intuitionistic inference engine \cite{cornelis2001compositional}
+intuitionistic inference engine \cite{cornelis2001compositional} %Que diferencias hay?
 
-implementation of a ifis, castillo \cite{castillo2007intuitionistic}
+implementation of a ifis, castillo \cite{castillo2007intuitionistic} %Por?
 
@@
 
-centroid of a type-2 fuzzy-set \cite{karnik2001centroid}
+centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
 
@@
 \section{Proposed Method}
-
+%(Mario)Is a Method? Extension? Implementation?
 The method, for now, consists on the procedures and elements
 necessary to construct a basic Intuitionistic Fuzzy Inference System
-(IFIS). This design was completed in order to make comparisons against
+(IFIS). %(Mario)Por que basic?
+%(Mario)Tal vez enumerarlas? cuales procedures son?
+This design was completed in order to make comparisons against
 classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
@@
 the classic FISs.
+%(Mario)Es el proposito del diseño comparar? Creo que puedes decir mejor algo como:
+%In order to assess the advantage of our proposal in terms of X
+%a comparassion with  Type-1 FIS, Interval Type-2 and General Type-2 FIS,
+%is presented.
+%que se vea que tiene su merito propio, y lo comparamos para
+%evaluar y comprobar su viabilidad
+%Lo de Design me ocasiona ruido, parece que fuera una implementación
+%Si no lo es, tal vez se puede decir algo como:
+%The proposed method was implemented in order to make.
 
-In many works, intuitionistic fuzzy sets (IFSs) are constructed by
-hand, by interviewing experts who assign memberships and
-non-memberships to each of the values of a set (such as in
+In many works, intuitionistic fuzzy sets (IFSs) are constructed manualy,
+by interviewing experts who assign memberships and
+non-memberships to each of the values of a set (such as in %to each of the members of a set?
 \cite{davarzani2013novel}). This work proposes a convenient way of
@@
 complement of the fuzzy set corresponding to a Gaussian MF.
+%(Mario)Al parecer lo que se está presentando es una manera automatizada de 
+% hacer IFSs? Si  es así, es más facil presentarlo
 
@@
 
-Two convenient ways of modifying the NMF and
-satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
+Two convenient ways of modifying a NMF and also
+satisfying (\ref{intuitionistic-interval}) are the following: 1) setting
 the mean and the standard deviation of the Gaussian functions to be
 the same, and only vary the $height$ of the NMF,
-as is depicted in Fig. \ref{ifs}; and 2) one can set different means and
+as is depicted in Fig. \ref{ifs}; and 2) setting different means and
 standard deviations of the Gaussian membership and non-membership
-functions, but the $height$ of the MF must be equal
+functions, while keeping the $height$ of the MF equal
 to $h_{mf} = 1 - h_{nmf}$, as this ensures that
@@
 
-The first step in an inference process in a classic FIS (a flow chart
+The first step of the inference process in a classic FIS (a flow chart
 for the process in an IFIS is given in Fig. \ref{flow-chart}) is to
 determine what membership corresponds to a given input, given a set of
+%(Mario)determine what particular membership function corresponds to a 
+% given input, given a set of 
 MFs. This is straightforward in a classic FIS, as the
@@
 which is described in (\ref{imembership}), and receives the name of
-$i\mu$ (intuitionistic membership).
+$i\mu$ (intuitionistic membership). %(Mario)Creo que este podría ser el titulo
 
@@
 
-The next step in the inference process is to perform an $\alpha$-cut
+The next step in the inference process is to perform an $\alpha$-cut % (Mario) La del FIS? aclaralo
 on the associated consequents to the antecedents that are activated by
@@
 consequents, in order to obtain a crisp number that represents
-it. There are a number of methods that can be used to defuzzify a
+it. There are a number of methods that can be used to defuzzify a %Aclara que en los tipo Mamdani
 fuzzy set, but the most frequently found in the literature is the
@@
 than a T2-FIS. The experiments presented in this work
-cannot prove this statement profoundly, as the results will only test for a
+cannot prove this statement profoundly, as the results will only be tested for a
 single situation, which is the prediction of a subset of the
@@
 
-Results can be found on https://github.com/amherag/wcci-2016-a
+The results of the experiment along with the code can be found on the 
+following public Github repository: https://github.com/amherag/wcci-2016-a
 

### 2016-01-08 paper.tex
4/5 Experiments

--- 2016-01-08 paper.tex
@@
 
+An implementation of the proposed method was developed using the
+programming language Clojure, and it is freely accessible at
+https://github.com/amherag/intuitionistic-fis. The T1-FISs and
+IT2-FISs were developed using Juzzy \cite{wagner2013juzzy}, which
+implements T1-FIS, IT2-FIS and GT2-FIS in Java.
+
+The Mackey-Glass time series benchmark was used in order to compare
+the performances of each of the FISs, and a Genetic Algorithm (GA) was
+used to optimize each of the FISs, so sub-optimal versions of each of
+the systems were used for the comparison.
+
+Every FIS uses the following rule base:
+
+\begin{enumerate}
+  \item if $t_{0}$ is $A_{1}$ then $p_{t+1}$ is $C_{1}$
+  \item if $t_{-6}$ is $A_{2}$ then $p_{t+1}$ is $C_{2}$
+  \item if $t_{-12}$ is $A_{3}$ then $p_{t+1}$ is $C_{3}$
+  \item if $t_{-18}$ is $A_{4}$ then $p_{t+1}$ is $C_{4}$
+\end{enumerate}
+
+where $t_{0}$, $t_{-6}$, $t_{-12}$, and $t_{-18}$ are points in the
+Mackey-Glass time series, $t_{0}$ is the present point, $t_{-6}$ is six
+points earlier than $t_{0}$, $t_{-12}$ is twelve points earlier, and
+$t_{-18}$ is eighteen points earlier. $p_{t+1}$ is the predicted value
+for the point $t_{1}$. $A_{1}$, $A_{2}$, $A_{3}$, and $A_{4}$ are
+antecedents, and $C_{1}$, $C_{2}$, $C_{3}$, and $C_{4}$ are
+consequents.
+
+The search space for the GA consists on eight tuples with the form $\langle
+mean, standard deviation \rangle$ for the T1-FIS, $\langle
+mean, standard deviation, height \rangle$ for the IFIS, $\langle
+mean, standard deviation 1, standard deviation 2 \rangle$ for the
+IT2-FIS with uncertain standard deviation, and $\langle
+mean 1, mean 2, standard deviation \rangle$ for the IT2-FIS with
+uncertain mean, where the means and standard deviations can take
+random real numbers from 0 to 100, and the height can take random real
+numbers from 0.8 to 1. Each of the individuals in the GA consists on
+eight tuples, one for each of the four antecedents and four
+consequents in a FIS. The rule base isn't optimized.
+
+Regarding the parameters of the GA, every FIS is optimized for 20
+generations, using 100 individuals as the initial population. The
+roulette wheel method is used as the selection operator. Five
+children are generated each generation and replace the five least
+fitted individuals in the population. For the mutation operator, each
+individual in the population has a chance of 1\% of suffering an
+alteration, which consists on replacing a list of tuples of arbitrary
+length from the individual with a
+
 % Comparisons against juzzy \cite{wagner2013juzzy}
@@
 % The rule base.
-
-\begin{enumerate}
-  \item if $t_{0}$ is $A_{1}$ then $p_{t+1}$ is $C_{1}$
-  \item if $t_{-6}$ is $A_{2}$ then $p_{t+1}$ is $C_{2}$
-  \item if $t_{-12}$ is $A_{3}$ then $p_{t+1}$ is $C_{3}$
-  \item if $t_{-18}$ is $A_{4}$ then $p_{t+1}$ is $C_{4}$
-\end{enumerate}
 

### 2016-01-08 paper.tex

@@
 %Empieza aquí 
+%-- (Amaury) Empezaré aquí
 There can be different types. Type-2 \cite{mendel2002type}, interval
@@
 
-%o incluso aquí
 Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}
@@
 % al parecer es por que Type-2 is time-consuming  
+%   --(Amaury)
+%% -- Sí y no. Hacerlo intuicionista le añade el concepto de
+%% indeterminación. No es un reemplazo del tipo-2, en realidad le
+%% añade cosas. Ahora, sí es parte de la justificación, ya que alguien
+%% puede optar por usar un tipo-1 intuicionista en lugar de un tipo-2
+%% por intervalos, por ejemplo, porque puede ser que gane performance
+%% parecido al de un tipo-2, sin tener el time-consuming de un
+%% tipo-2. Igual puede haber un tipo-2 intuicionista.
+
 % Esto si:
@@
 % Después lo clasico de como esta dividido el trabajo
+%% (Amaury): Ok! Voy a dar una descripción básica, ya que en la
+%% sección de preliminares es donde explico a fondo
+
 \section{Related Work}
@@
 
-intuitionistic inference engine \cite{cornelis2001compositional} %Que diferencias hay?
+intuitionistic inference engine \cite{cornelis2001compositional} %Que
+                                %diferencias hay?
+%% (Amaury): oh, sí voy a poner las diferencias. Nomás puse todo esto
+%% para acordarme :D
 
-implementation of a ifis, castillo \cite{castillo2007intuitionistic} %Por?
+implementation of a ifis, castillo \cite{castillo2007intuitionistic}
+% Por?  
+%% (A): Porque es lo más cercano a un FIS mamdani intuicionista. al
+%% menos de lo que encontré.
 
@@
 centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
+%% Porque yo propongo una fórmula para calcular centroide de un IFS, y
+%% como la competencia de un IFS sería un fuzzy set tipo 2, iba a
+%% hablar un poco de eso
 
@@
 %(Mario)Is a Method? Extension? Implementation?
+%% (A): No lo había pensado en realidad. Es que siempre le llamo
+%% Proposed Method jajajaaj. Aunque creooo que sí es un método. Es un
+%% método para hacer un sistema de inferencia difusa con conjuntos
+%% difusos intuicionistas
 The method, for now, consists on the procedures and elements
@@
 (IFIS). %(Mario)Por que basic?
+%% (A): Basic porque no añado que puedas poner OR en las reglas, no
+%% pongo otros métodos de defuzzificación, no pongo más funciones de
+%% membresía (triangulares, etc.). Explicaré eso (y)
 %(Mario)Tal vez enumerarlas? cuales procedures son?
-This design was completed in order to make comparisons against
+%% (A): Los procedures son los que están en el diagramita, y las
+%% explico abajo. Aun así las enumero?
+An implementation was completed in order to make comparisons against
 classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
@@
 %is presented.
+
+%% (A): Ok, me gusta.
+
 %que se vea que tiene su merito propio, y lo comparamos para
@@
 %The proposed method was implemented in order to make.
+
+%% (A): Ya lo cambié al principio, pero el design en "prove that the
+%% design was viable" no sé si cambiarlo
 
@@
 % hacer IFSs? Si  es así, es más facil presentarlo
+%% Si se hacen automatizadamente para poder compararlo con el tipo-1 y
+%% tipo-2, pero no es el objetivo del trabajo.
 
@@
 for the process in an IFIS is given in Fig. \ref{flow-chart}) is to
-determine what membership corresponds to a given input, given a set of
+determine what grade of membership corresponds to a given input, given a set of
 %(Mario)determine what particular membership function corresponds to a 
 % given input, given a set of 
+%% (A): Es grade of membership, perdón. De hecho hay ese error en
+%% otras partes, tengo que cambiarlo.
 MFs. This is straightforward in a classic FIS, as the
@@
 which is described in (\ref{imembership}), and receives the name of
-$i\mu$ (intuitionistic membership). %(Mario)Creo que este podría ser el titulo
+$i\mu$ (intuitionistic membership). %(Mario)Creo que este podría ser
+                                %el titulo
+%% (A): Para poder hacer un FIS intuicionista, necesité el
+%% intuitionistic membership y el intuitionistic center of area. Cómo
+%% propone el título?
 
@@
 consequents, in order to obtain a crisp number that represents
-it. There are a number of methods that can be used to defuzzify a %Aclara que en los tipo Mamdani
+it. There are a number of methods that can be used to defuzzify a
+% Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
 fuzzy set, but the most frequently found in the literature is the

### 2016-01-08 paper.tex
Done: Experiments, Results, Conclusion, Future Work

@@
 \section{Proposed Method}
+\label{proposed-method}
 %(Mario)Is a Method? Extension? Implementation?
@@
 fuzzy interpretation. An example of an IFS is depicted in
-Fig. \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
+Figure \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
 satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
@@
 the same, and only vary the $height$ of the NMF,
-as is depicted in Fig. \ref{ifs}; and 2) setting different means and
+as is depicted in Figure \ref{ifs}; and 2) setting different means and
 standard deviations of the Gaussian membership and non-membership
@@
 (\ref{intuitionistic-interval}) is satisfied. An example of the latter
-case is shown in Fig. \ref{ifs-diff-mu-sd}. To clarify, the $height$
+case is shown in Figure \ref{ifs-diff-mu-sd}. To clarify, the $height$
 of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
@@
 The first step of the inference process in a classic FIS (a flow chart
-for the process in an IFIS is given in Fig. \ref{flow-chart}) is to
+for the process in an IFIS is given in Figure \ref{flow-chart}) is to
 determine what grade of membership corresponds to a given input, given a set of
@@
 A comparison of a MF (red line) against an intuitionistic
-membership function (blueline) is shown in Fig.
+membership function (blueline) is shown in Figure
 \ref{if-membership}. The parameters for both the MF and NMF are $\mu =
@@
 but a smaller standard deviation. A more elaborated example is shown
-in Fig. \ref{if-membership-drastic}, where the parameters of the MF
+in Figure \ref{if-membership-drastic}, where the parameters of the MF
 are $\mu = 50$, $SD = 15$ and $h = 0.8$, and the parameters of the NMF
@@
 $\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} =
-0.6$, is depicted in Fig. \ref{alpha-cut-example}.
+0.6$, is depicted in Figure \ref{alpha-cut-example}.
 
@@
 and B, as in (\ref{union-operator}). An example of an union of three
-IFSs is shown in Fig. (\ref{ifs-union}).
+IFSs is shown in Figure (\ref{ifs-union}).
 
@@
 
-Fig. \ref{if-coa-vs-coa} shows the plot of the defuzzification of
+Figure \ref{if-coa-vs-coa} shows the plot of the defuzzification of
 several IFSs with $CoA$ (red line) and $iCoA$ (blue line), with means set
@@
 The Mackey-Glass time series benchmark was used in order to compare
-the performances of each of the FISs, and a Genetic Algorithm (GA) was
+the performances of each of the FISs regarding their time series
+forecasting capabilities, and a Genetic Algorithm (GA) was
 used to optimize each of the FISs, so sub-optimal versions of each of
@@
 
+The dataset consists of 100 data points for training, and 50 data
+points for testing. These data points were scaled, such that the
+resulting data points range from 0 to 100. The scaling process was
+performed by applying (\ref{scaling}) over each of the data points in
+the union of the training and testing subsets. The reason behind this
+preprocessing is that the implementation of the IFIS works with inputs
+ranging from 0 to 100, but the Mackey-Glass time series' data points
+range from 0 to about 1.4. This does not alter the measurement of the
+error produced by each of the FISs, as the outputs from the FISs are
+also scaled from 0 to 100.
+
+\begin{equation}
+  \label{scaling}
+  S(p) = 100 \frac{p - min(P)}{max(P) - min(P)}
+\end{equation}
+
 The search space for the GA consists on eight tuples with the form $\langle
@@
 alteration, which consists on replacing a list of tuples of arbitrary
-length from the individual with a
+length from the affected individual with a list of tuples of the same
+length from another random individual in the population. Finally, the
+crossover operator takes random genetic material from two individuals
+and creates a child of the same length as its parents. The genetic
+material cannot be repeated, can be of different proportions from each
+of the parents, and the original order isn't preserved. For example,
+given the individuals $A = <1, 2, 3, 4>$ and $B = <5, 6, 7, 8>$, a
+possible child is $C = <8, 1, 7, 5>$. This operator was developed
+because it proved by trial and error that it created more diversity in
+the children than other operators such as one-point or two-point
+crossover.
+
+To obtain the performance of a particular individual, a FIS is created
+using the parameters represented by its genetic material. The created
+FIS is then evaluated with each of the inputs in the training dataset
+(100 sets of four data points: $t_{0}$, $t_{-6}$, $t_{-12}$, and
+$t_{-18}$). The outputs (i.e. the 100 predicted values) for each of
+the inputs are then scaled from 0 to 100, as was mentioned before, so
+a Mean Squared Error (MSE) can be obtained by comparing the predicted values
+to the scaled Mackey-Glass' points ($p_{t+1}$). Individuals with lower
+MSEs are said to be performing better.
+
+Finally, the better performing individual after the 20 generations in
+the GA is evaluated using the training and testing datasets, and the
+resulting MSEs are used as the result of one experiment. In total, 60
+experiments were performed for the T1-IFIS, 60 for the T1-FIS, 100 for
+the IT2-FIS with uncertain mean, and 300 for the IT2-FIS with
+uncertain standard deviation.
 
@@
 \section{Results}
+\label{results}
 
-The results of the experiment along with the code can be found on the 
-following public Github repository: https://github.com/amherag/wcci-2016-a
+The full results (CSV files containing the MSE for each of the
+experiments) along with the Clojure source code used to obtain the
+data presented in this section can be found on the following public
+Github repository: https://github.com/amherag/wcci-2016-a.
+
+Initially, 60 experiments were performed for every FIS, but that
+number of experiments didn't provide enough statistical data for the
+IT2-FISs in order to make a conclusion. For the IT2-FIS with uncertain
+mean, 100 experiments were needed to provide enough statistical data
+to conclude what FIS performed better, and for the IT2-FIS with
+uncertain standard deviation, 300 experiments were needed. To clarify,
+all of the comparisons were against the T1-IFIS.
+
+Table \ref{hypothesis-tests-training} summarizes the results obtained
+for each of the FISs in the training stage, as well as the t-value
+obtained when calculating a Student's t-test. The same structure is
+followed in Table \ref{hypothesis-tests-testing}, which shows the
+results obtained for each of the FISs in the testing stage.
 
@@
     \hline
-    T1 iFIS & 89.50 & 25.36 & 60 & \\
+    T1-IFIS & 89.50 & 25.36 & 60 & \\
     \hline
-    T1 FIS & 108.05 & 23.47 & 60 & -4.1584 \\
+    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 \\
     \hline
-    IT2 FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 \\
+    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 \\
     \hline
-    IT2 FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 \\
+    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 \\
     \hline
@@
   \caption{Hypothesis Tests for the Testing Stage}
-  \label{hypothesis-tests}
+  \label{hypothesis-tests-testing}
   \centering
@@
     \hline
-    T1-iFIS & 160.99 & 65.70 & 60 & \\
+    T1-IFIS & 160.99 & 65.70 & 60 & \\
     \hline
@@
 
-This work mainly focuses on proving that the design is viable, but it
-also proves that at least in some cases the intuitionistic fis can
-out-perform the t1 and t2.
+As the results in Section \ref{results} demonstrate, the T1-IFIS
+outperforms the T1-FIS, IT2-FIS with uncertain mean, and IT2-FIS with
+uncertain standard deviation. These results sustain the claim that the
+intuitionistic grade of membership ($i\mu$), and the intuitionistic center
+of area ($iCoA$), proposed in Section \ref{proposed-method} allows the
+creation of a T1-IFIS that can perform better than a classic T1-FIS
+and an IT2-FIS.
+
+Several derivative works can result from the ideas presented in this paper. For
+example, the proposed T1-IFIS can be tested using several
+benchmarks, other than the Mackey-Glass time series. Also, this work
+should inspire the creation of Type-2 Intuitionistic Fuzzy Inference
+Systems (both the interval and general types).
 
@@
 
-We want to create a toolbox such as \cite{castro2007interval}
-We want to experiment with other data sets.
-We want to speed up the algorithm.
-We want to experiment with generalized type-2.
+The current implementation of the proposed method lacks a Graphical User
+Interface (GUI) where a research can conveniently design an IFIS, such as
+Matlab's Type-1 Fuzzy Logic toolbox, or the Type-2 Fuzzy Logic toolbox
+developed by J. R. Castro $et al.$ \cite{castro2007interval}. The
+development of a GUI is planned as a next step, so researchers without
+a background in the programming langague Clojure can use the
+implementation for their works.
+
+In theory, an implementation of the proposed method should be faster
+than T2-FISs, and slower than T1-FISs (although this difference should
+be negligible), but the current implementation performs worse, in
+terms of time, than a general T2-FIS. This has to be solved in order
+to speed up the experiments conducted, and to encourage other
+researchers to use the implementation.
 

### 2016-01-13 paper.tex
Ejemplo
Cambio a comentario

@@
 \begin{abstract}
-
+The concepts of intuitionistic membership, and intuitionistic center of
+area are proposed in this work, in order to propose a novel method for
+implementing an intuitionistic fuzzy inference system. The proposed
+method was implemented and compared against type-1 fuzzy inference
+systems and interval type-2 fuzzy inference systems, with uncertain
+means and uncertain standard deviations, by using the
+Mackey-Glass time series benchmark. A genetic algorithm was used to
+optimize the parameters of each of the methods being compared, and the
+results show that the intuitionistic fuzzy inference system performs
+better than the other methods.
 \end{abstract}
@@
 
-What is a fuzzy set? \cite{zadeh1965fuzzy}
+Fuzzy sets were created as an extension to traditional sets, with
+uncertainty in mind, by L. A. Zadeh in 1965 \cite{zadeh1965fuzzy}. This uncertainty allows an
+element to be associated with a grade of membership that indicates
+how much that element belongs to a set, i.e., instead of
+belonging to a set (true, or 1), or not belonging (false, or 0),
+such element can belong in a grade from 0 to 1, and this is known as
+fuzzy logic \cite{klir1995fuzzy}.
 
-What is fuzzy logic? \cite{klir1995fuzzy}
+A derivation of logical conclusions can be performed by using premises
+that are assumed to be true, and this is known as inference, in
+traditional logic. The same
+technique can be extended to use fuzzy premises. In this case, all the
+premises hold a grade of truthiness, and a fuzzy conclusion is derived
+from the process. A popular method for performing such fuzzy inferences is a
+Mamdani Fuzzy Inference System (FIS) \cite{mamdani1975experiment},
+where the inputs are associated with fuzzy sets, and the outputs are
+fuzzy sets themselves, which can be converted to crisp numbers
+(this process is usually called \textit{defuzzification}). Other types of
+fuzzy inference engines exist, such as Takagi-Sugeno-Kang  (TSK)
+\cite{takagi1985fuzzy} and Tsukamoto \cite{tsukamoto1979approach}.
 
-Types of fuzzy sets. Mendel book \cite{mendel2001uncertain}
+Fuzzy sets were initially criticized because they were said to
+not be able to appropriately represent uncertainty. This problem was
+addressed by L. A. Zadeh in 1975 \cite{zadeh1975concept} by creating the
+concept of Type-2 Fuzzy Sets (T2-FS). This extension to type-1 fuzzy sets allowed the creation of
+type-2 fuzzy inference systems (T2-FIS) \cite{mendel2002type}, and those systems that used the
+traditional fuzzy sets are now called Type-1 Fuzzy Inference Systems
+(T1-FIS). T2-FIS have been proved to work better than T1-FIS in many
+situations, often problems that involve high levels of uncertainty, such as
+noisy data.
 
-What is a fuzzy inference system?
+Another extension to fuzzy sets, called Intuitionistic Fuzzy Sets
+(IFS), was proposed by K. T. Atanassov
+\cite{atanassov1986intuitionistic}. This extension adds the concepts
+of indeterminacy and non-membership to traditional fuzzy sets. In
+traditional fuzzy sets, the non-membership of an element is always the
+complement of the membership, but in an IFS, the non-membership can be
+represented by lower values (a deeper explanation of IFS is given in
+Section \ref{preliminaries}). Whenever the sum of the membership and
+the non-membership is less than 1, indeterminacy emerges, which
+represents the grade of uncertainty of an element of being or not
+being a member of a given set, with certain grade of membership. The
+concept of indeterminacy allows an expression such as ``This is
+somewhat tall, although I'm not very sure about my opinion.''
 
-%Empieza aquí 
-%-- (Amaury) Empezaré aquí
-There can be different types. Type-2 \cite{mendel2002type}, interval
-t2 \cite{liang2000interval} and \cite{mendel2006interval}
+The use of IFSs in a traditional FIS should enable the handling of more
+uncertainty, and one could prefer an Intuitionistic FIS (IFIS) to obtain
+better accuracies without sacrificing time performance, as
+inferences in a T2-FIS are very time consuming compared to a
+T1-FIS. This is a consequence of the complex type
+reducing procedure that is involved in the defuzzification stage in a
+T2-FIS \cite{mendel2001uncertain}. Several improvements to the
+algorithms involved in the inference process in a T2-FIS have been proposed
+to alleviate this problem, such as the Karnik-Mendel algorithm
+\cite{wu2009enhanced} and shadowed sets
+\cite{pedrycz1998shadowed}. Nevertheless, a T2-FIS is usually several
+times slower than a T1-FIS. Because of this time performance impact,
+many works that require handling more uncertainty than a T1-FIS
+use a particular case of T2-FIS, the Interval T2-FIS (IT2-FIS)
+\cite{mendel2006interval}, which is faster than a general T2-FIS. A Type-1
+Intuitionistic FIS (T1-IFIS) should perform better than a T1-FIS in terms
+of accuracy (in problems involving data with high levels of
+uncertainty), and should be faster than a T2-FIS. Furthermore, IFSs
+can be implemented as part of a T2-FIS, giving as a result a T2-IFIS.
 
-Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}
+This work proposes a method to implement IFSs in a Mamdani FIS to
+obtain a Mamdani IFIS, and presents results that prove the method as a
+viable design to implement an effective IFIS. The reader can find
+related works in Section \ref{related-work}. Some preliminaries are
+explained in Section \ref{preliminaries} in order to better comprehend
+the proposed method in Section \ref{proposed-method}. Experiments were
+conducted to prove the viability of the proposed method, and they are
+explained in Section \ref{experiments}. The results of the conducted
+experiments are shown and explained in Section \ref{results}, and a
+conclusion about the results is presented in Section
+\ref{conclusion}. Finally, a description of the future work can be
+found in Section \ref{future-work}.
 
-What is a intuitionistic fuzzy set? \cite{atanassov1986intuitionistic}
-\cite{atanassov2003intuitionistic} \cite {despi2013generalised}
+%What is a intuitionistic fuzzy set? \cite{atanassov1986intuitionistic}
+%\cite{atanassov2003intuitionistic} \cite {despi2013generalised}
 
@@
 \section{Related Work}
+\label{related-work}
 
@@
 \section{Preliminaries}
+\label{preliminaries}
 
@@
 the mean and the standard deviation of the Gaussian functions to be
-the same, and only vary the $height$ of the NMF,
+the same, and only vary the \textit{height} of the NMF,
 as is depicted in Figure \ref{ifs}; and 2) setting different means and
 standard deviations of the Gaussian membership and non-membership
-functions, while keeping the $height$ of the MF equal
+functions, while keeping the \textit{height} of the MF equal
 to $h_{mf} = 1 - h_{nmf}$, as this ensures that
 (\ref{intuitionistic-interval}) is satisfied. An example of the latter
-case is shown in Figure \ref{ifs-diff-mu-sd}. To clarify, the $height$
+case is shown in Figure \ref{ifs-diff-mu-sd}. To clarify, the \textit{height}
 of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
-$height$ of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.
+\textit{height} of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.
 
@@
 \ref{if-membership}. The parameters for both the MF and NMF are $\mu =
-50$ and $SD = 15$, but the $height$ for the NMF is set at $0.5$. This
+50$ and $SD = 15$, but the \textit{height} for the NMF is set at \textit{0.5}. This
 results in an intuitionistic MF that appears to have the same mean,
@@
 
-The next step in the inference process is to perform an $\alpha$-cut % (Mario) La del FIS? aclaralo
-on the associated consequents to the antecedents that are activated by
-the inputs. In a classic FIS, this process is straightforward, as the
-memeberships in a fuzzy set representing a consequent are ``cut'' by
-following (\ref{alpha-cut}) for every element in a fuzzy set
-representing a consequent. In an intuitionistic MF, one can follow
-the same procedure in order to obtain the $\alpha$-cut in the MF part,
-but to obtain the $\alpha$-cut in the NMF, (\ref{nmf-alpha-cut}) must
-be followed. In (\ref{nmf-alpha-cut}), the counterintuitive part is
-that one has to find the corresponding $\nu$ for a given
-$\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} =
-0.6$, is depicted in Figure \ref{alpha-cut-example}.
+The next step in the inference process is to perform an $\alpha$-cut % (Mario)
+La del FIS? aclaralo on the associated consequents to the antecedents that are
+activated by the inputs. In a classic FIS, this process is straightforward, as
+the memeberships in a fuzzy set representing a consequent are ``cut'' by
+following (\ref{alpha-cut}) for every element in a fuzzy set representing a
+consequent. In an intuitionistic MF, one can follow the same procedure in order
+to obtain the $\alpha$-cut in the MF part, but to obtain the $\alpha$-cut in
+the NMF, (\ref{nmf-alpha-cut}) must be followed. In (\ref{nmf-alpha-cut}), the
+counterintuitive part is that one has to find the corresponding $\nu$ for a
+given $\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} = 0.6$,
+is depicted in Figure \ref{alpha-cut-example}.
 
@@
 it. There are a number of methods that can be used to defuzzify a
-% Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
+% Aclara que en los tipo Mamdany %% (A): ahhhhh cierto, cierto
 fuzzy set, but the most frequently found in the literature is the
@@
 \section{Experiments}
+\label{experiments}
 
@@
 the systems were used for the comparison.
+%M: En esta seccion creo que se
 
@@
 \end{enumerate}
-
 where $t_{0}$, $t_{-6}$, $t_{-12}$, and $t_{-18}$ are points in the
@@
 
-Table \ref{hypothesis-tests-training} summarizes the results obtained
+Table \ref{first-hypothesis-tests-training} summarizes the results obtained
 for each of the FISs in the training stage, as well as the t-value
 obtained when calculating a Student's t-test. The same structure is
-followed in Table \ref{hypothesis-tests-testing}, which shows the
+followed in Table \ref{first-hypothesis-tests-testing}, which shows the
 results obtained for each of the FISs in the testing stage.
@@
   \renewcommand{\arraystretch}{1.3}
-  \caption{Hypothesis Tests for the Training Stage}
-  \label{hypothesis-tests-training}
+  \caption{Hypothesis Tests for the Training Stage, First Experiment}
+  \label{first-hypothesis-tests-training}
   \centering
@@
     \hline
-    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value\\
+    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI \\
     \hline
-    T1-IFIS & 89.50 & 25.36 & 60 & \\
+    T1-IFIS & 89.50 & 25.36 & 60 &  & \\
     \hline
-    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 \\
+    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 & > 99.9\% \\
     \hline
-    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 \\
+    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 & > 99.9\% \\
     \hline
-    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 \\
+    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 & > 99.9\% \\
+    \hline
+  \end{tabular}
+\end{table}
+
+% con 400
+\begin{table}[!t]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Hypothesis Tests for the Training Stage, Second Experiment}
+  \label{second-hypothesis-tests-training}
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI\\
+    \hline
+    T1-IFIS & 76.22 & 16.90 & 400 & & \\
+    \hline
+    T1-FIS & 85.69 & 19.68 & 400 & -7.3013 & > 99.9\% \\
+    \hline
+    IT2-FIS (\(\mu\)) & 85.93 & 19.12 & 400 & -7.6102 & > 99.9\%\\
+    \hline
+    IT2-FIS (SD) & 99.78 & 19.04 & 400 & -18.508 & > 99.9\% \\
     \hline
@@
   \renewcommand{\arraystretch}{1.3}
-  \caption{Hypothesis Tests for the Testing Stage}
-  \label{hypothesis-tests-testing}
+  \caption{Hypothesis Tests for the Testing Stage, First Experiment}
+  \label{first-hypothesis-tests-testing}
   \centering
@@
     \hline
-    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value\\
+    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI \\
     \hline
-    T1-IFIS & 160.99 & 65.70 & 60 & \\
+    T1-IFIS & 160.99 & 65.70 & 60 &  & \\
     \hline
-    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 \\
+    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 & > 99.2\%\\
     \hline
-    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 \\
+    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 & > 97.8\% \\
     \hline
-    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 \\
+    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 & > 91.4\% \\
+    \hline
+  \end{tabular}
+\end{table}
+
+% con 400
+\begin{table}[!t]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Hypothesis Tests for the Testing Stage, Second Experiment}
+  \label{second-hypothesis-tests-testing}
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI\\
+    \hline
+    T1-IFIS & 139.38 & 95.75 & 400 &  &  \\
+    \hline
+    T1-FIS & 152.26 & 126.47 & 400 & -1.6239 & > 89.4\% \\
+    \hline
+    IT2-FIS (\(\mu\)) & 154.37 & 119.92 & 400 & -1.9536 & > 94.8\% \\
+    \hline
+    IT2-FIS (SD) & 175.04 & 136.91 & 400 & -4.1492 & > 99.9\%\\
     \hline
@@
 \section{Conclusion}
+\label{conclusion}
 
@@
 \section{Future Work}
+\label{future-work}
 
@@
 Matlab's Type-1 Fuzzy Logic toolbox, or the Type-2 Fuzzy Logic toolbox
-developed by J. R. Castro $et al.$ \cite{castro2007interval}. The
+developed by J. R. Castro \textit{et al.} \cite{castro2007interval}. The
 development of a GUI is planned as a next step, so researchers without

### 2016-01-13 paper.tex
borre comentarios.
type-3

@@
 %
-% \usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
 
@@
 method was implemented and compared against type-1 fuzzy inference
-systems and interval type-2 fuzzy inference systems, with uncertain
+systems and interval type-3 fuzzy inference systems, with uncertain
 means and uncertain standard deviations, by using the

### 2016-01-13 paper.tex
Revert "borre comentarios."
This reverts commit cfab30905c92f192c38d9ff72deb29df5613f28f.

--- 2016-01-13 paper.tex
@@
 method was implemented and compared against type-1 fuzzy inference
-systems and interval type-2 fuzzy inference systems, with uncertain
+systems and interval Type-2 fuzzy inference systems, with uncertain
 means and uncertain standard deviations, by using the

### 2016-01-13 paper.tex
Revert "Ejemplo"
This reverts commit 9a6452255f89a5e01a483b19ee70778ccfc445ba.
back

--- 2016-01-13 paper.tex
@@
 method was implemented and compared against type-1 fuzzy inference
-systems and interval type-3 fuzzy inference systems, with uncertain
+systems and interval Type-2 fuzzy inference systems, with uncertain
 means and uncertain standard deviations, by using the

### 2016-01-18 paper.tex
Corrected
closes #9
Done: Preliminaries

@@
 
+A goal of this work is to propose a method to design a Mamdani IFIS that is
+similar in construction to the traditional Mamdani FIS. There are works
+that have successfully constructed inference engines that use IFS
+instead of traditional FS, but most of these works are not Mamdani
+systems. Another goal is to fully integrate the concept of
+non-membership into the inference process in a meaningful way,
+considering how the non-membership concept should affect the process.
+
+A straightforward method to obtain an inference by using IFS is to
+apply the implication operator over a number of IFS. This operator,
+proposed by K. T. Atanassov, is described in
+\cite{atanassov2013intuitionistic} as in (\ref{ifs-implication})
+
+% intuitionistic fuzzy set
+\begin{equation}
+  \label{ifs-implication}
+  \begin{aligned}
+  A \implies B = & \{ \langle x, max(\nu_{A} (x), \mu_{B}(x)),\\
+  &\quad min(\mu_{A} (x), \nu_{B} (x)) \rangle | x \in E \}
+\end{aligned}
+\end{equation}
+
+C. Cornelis and G. Deschrijver \cite{cornelis2001compositional}
+generalize the Compositional Rule of Inference to IFSs
+%intuitionistic inference engine \cite{cornelis2001compositional} %Que
+                                %diferencias hay?
+
+A method for inference in approximate reasoning based on normal
+intuitionistic fuzzy sets \cite{bustince1995method}
+
+A Method and Electronic Circuit for Intuitionistic Fuzzy Inference
+\cite{marinov2005method}
+An intuitionistic fuzzy system for time series analysis in plant
+monitoring and diagnosis \cite{castillo2007intuitionistic}
+
+% Applications
+Intuitionistic fuzzy sets in some medical applications
+\cite{szmidt2001intuitionistic}
+Switching between type-2 fuzzy sets and intuitionistic fuzzy sets: an
+application in medical diagnosis \cite{own2009switching}
+Intuitionistic preference relations and their application in group
+decision making \cite{xu2007intuitionistic}
+An application of intuitionistic fuzzy information for handwritten
+Arabic word recognition \cite{baccour2008application}
 Application of intuitionistic fuzzy sets, bacillus colonies
@@
 
-Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}
-
-intuitionistic inference engine \cite{cornelis2001compositional} %Que
-                                %diferencias hay?
-%% (Amaury): oh, sí voy a poner las diferencias. Nomás puse todo esto
-%% para acordarme :D
-
-implementation of a ifis, castillo \cite{castillo2007intuitionistic}
 % Por?  
@@
 
-more inference \cite{bustince1995method}
+%%%%%%%%Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}
 
-centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
+%%%%%%%%centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
 %% Porque yo propongo una fórmula para calcular centroide de un IFS, y
@@
 
-and even more inference \cite{marinov2005method}
-
-Intuitionistic control washing machines \cite{akram2014intuitionistic}
-
 \section{Preliminaries}
@@
 
-Define in more detail intuitionistic fuzzy sets.
-
-Formulas and basic explanation (below) \cite{atanassov2013intuitionistic}
+An IFS, as defined by K. T. Atanassov in
+\cite{atanassov2013intuitionistic}, is usually represented by a
+capital letter (as a traditional set) and an uppercase star,
+e.g. $A^{*}$. The definition for an IFS is expressed in
+(\ref{ifs-definition}), where $x$ is an element of the set,
+$\mu_{A}(x)$ is the membership for that element in the set, and
+$\nu_{A}(x)$ is the non-membership for that element in the set. For
+every element in an IFS, the interval defined in
+(\ref{intuitionistic-interval}) must be satisfied. If for every
+element in an IFS $\mu_{A}(x) + \nu_{A}(x)$ is equal to 1, then this
+IFS represents an ordinary fuzzy set, and it is defined by
+(\ref{ifs-form}).
 
@@
 \begin{equation}
+  \label{ifs-definition}
   A^{*} = \{\langle x, \mu _{A} (x), \nu _{A} (x) \rangle | x \in E\}
@@
 
+If for a given IFS $\mu_{A}(x) + \nu_{A}(x) < 1$, then the concept of
+indeterminacy (also found in the literature as non-determinacy and
+hesitancy) arises. Indeterminacy can be described as the
+uncertainty about the uncertainty, or how certain one can be about the
+membership of an element in a given set. This can be confused by the
+footprint of uncertainty (FOU) found in T2-FS, which could also be
+described as the uncertainty about the uncertainty, but in this case,
+the FOU represents a set of values that the membership of an element
+in a given T2-FS is taking. For example, one could add indeterminacy
+to a T2-FS, and the indeterminacy would represent how certain or
+uncertain is the FOU in the T2-FS. For every element $x$, the
+indeterminacy $\pi$ is defined as in (\ref{fs-as-ifs-if}).
+
 % if
@@
 \end{equation}
+
+% Ya lo menciono en el método propuesto
+
+% Lastly, in the proposed method, the intuitionistic membership
+% functions (IMF) representing the consequents need to be
+% aggregated. This aggregation can be done by applying the union
+% operator over the different IFS. This operator is defined in
+% \ref{atanassov2013intuitionistic} as in (\ref{ifs-union}).
 
@@
 it. There are a number of methods that can be used to defuzzify a
-% Aclara que en los tipo Mamdany %% (A): ahhhhh cierto, cierto
+% Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
 fuzzy set, but the most frequently found in the literature is the

### 2016-01-18 paper.tex
Done: Related Work

@@
 % and later.
+
+\usepackage{flushend}
 
@@
 
-C. Cornelis and G. Deschrijver \cite{cornelis2001compositional}
-generalize the Compositional Rule of Inference to IFSs
-%intuitionistic inference engine \cite{cornelis2001compositional} %Que
-                                %diferencias hay?
+Implications using fuzzy sets can be extended to compositions of rules of
+inference. A work that describes the compositional rule of inference
+using fuzzy sets, and the extension of the compositional rule of
+inference using IFSs, is the one by C. Cornelis and G. Deschrijver
+\cite{cornelis2001compositional}.
 
-A method for inference in approximate reasoning based on normal
-intuitionistic fuzzy sets \cite{bustince1995method}
+H. Bustince et al. \cite{bustince1995method} propose a method to
+perform inference using IFSs by using t-norm and t-conorm based on max
+and min operators. This work resembles the foundations of a Mamdani
+FIS. Another example is the work by M. Marinov and K. T. Atanassov
+\cite{marinov2005method}, which implements an electronic circuit
+capable of performing intuitionistic fuzzy inference, and describes
+the computer pseudo-code that must be followed in order to implement
+the method.
 
-A Method and Electronic Circuit for Intuitionistic Fuzzy Inference
-\cite{marinov2005method}
-An intuitionistic fuzzy system for time series analysis in plant
-monitoring and diagnosis \cite{castillo2007intuitionistic}
+The closest to a Mamdani IFIS that the authors of this work could
+find, was the work by O. Castillo et
+al. \cite{castillo2007intuitionistic}. The authors implement an IFIS
+by considering the membership functions and the non-membership
+functions as traditional fuzzy sets. In the end, the output of the FIS
+is calculated as a linear combination of the two fuzzy sets, by using
+(\ref{linear-combination})
 
-% Applications
-Intuitionistic fuzzy sets in some medical applications
-\cite{szmidt2001intuitionistic}
-Switching between type-2 fuzzy sets and intuitionistic fuzzy sets: an
-application in medical diagnosis \cite{own2009switching}
-Intuitionistic preference relations and their application in group
-decision making \cite{xu2007intuitionistic}
-An application of intuitionistic fuzzy information for handwritten
-Arabic word recognition \cite{baccour2008application}
-Application of intuitionistic fuzzy sets, bacillus colonies
-recognition \cite{davarzani2013novel}
+\begin{equation}
+  \label{linear-combination}
+  IFS = (1-\pi)FS_{\mu} + \pi FS_{v}
+\end{equation}
 
-% Por?  
-%% (A): Porque es lo más cercano a un FIS mamdani intuicionista. al
-%% menos de lo que encontré.
+The problem with this approach is that an IFS is being defined as two
+separate traditional fuzzy sets, and the non-membership or the
+indeterminacy is not affecting the membership of an element in a
+meaningful way. In contrast, the present work proposes the use of the
+intuitionistic membership in order to affect the firing strength that
+will activate a consequent, and the use of the intuitionistic center
+of area for obtaining a defuzzification of the aggregation of the
+consequents.
 
-%%%%%%%%Alpha cut \cite{sharma2011cut} \cite{sharma2011cutgroups}
+Another proposal that is being made indirectly in this work, is the
+way in which an IFS is represented. Most works represent an IFS as a
+lattice (as in \cite{deschrijver2004representation} and
+\cite{despi2013generalised}), but this work proposes a variation of the
+standard way of representing a fuzzy set. Some works use
+this way of representing an IFS (as in
+\cite{davarzani2013novel}). The proposal in this paper is to use the
+same convenient membership functions usually found in the design of
+traditional FISs, such as triangular or Gaussian membership functions,
+but using the complement of these functions to represent the
+non-membership function.
 
-%%%%%%%%centroid of a type-2 fuzzy-set \cite{karnik2001centroid} %Por?
-%% Porque yo propongo una fórmula para calcular centroide de un IFS, y
-%% como la competencia de un IFS sería un fuzzy set tipo 2, iba a
-%% hablar un poco de eso
+The proposed method is tested by using the Mackey-Glass time series
+benchmark, and therefore, an application of an IFIS is to use it for
+forecasting tasks. Other fields where IFSs have been used are: medical
+applications, as in the works by E. Szmidt and K. Janusz
+\cite{szmidt2001intuitionistic}, H. Davarzani and
+K. M. Amiri\cite{davarzani2013novel}, and C. M. Own
+\cite{own2009switching}; group decision making, as in the work by
+Z. Xu \cite{xu2007intuitionistic}; and handwritten word recognition,
+as in the work by L. Baccour et al. \cite{baccour2008application}.
 
@@
 
-The dataset consists of 100 data points for training, and 50 data
-points for testing. These data points were scaled, such that the
+The dataset consists of 500 data points for training, and 500 data
+points for testing. These data points are ordered, as it is a time
+series, and the first subset is for training and the second dataset is
+for testing. These data points are scaled, such that the
 resulting data points range from 0 to 100. The scaling process was
@@
 
-Initially, 60 experiments were performed for every FIS, but that
-number of experiments didn't provide enough statistical data for the
-IT2-FISs in order to make a conclusion. For the IT2-FIS with uncertain
-mean, 100 experiments were needed to provide enough statistical data
-to conclude what FIS performed better, and for the IT2-FIS with
-uncertain standard deviation, 300 experiments were needed. To clarify,
-all of the comparisons were against the T1-IFIS.
+A total of 400 runs were performed for every FIS. The decision for
+such a high number of runs was because of trial and error. Initially,
+the IFIS was being tested with a subset of the Mackey-Glass time
+series of 100 points for training, and 50 for testing. This decision
+was made as a consequence of the high computational time required to
+process the traditional sizes of the subsets. Some of the
+comparisons were successful, but others, especially against the
+T2-FIS, were lacking statistical data in order to obtain a decisive
+conclusion. In the end, the IT2-FIS with uncertain mean and the
+IT2-FIS with uncertain standard deviation required a total of 100 and
+300 runs, respectively. This led to the decision of performing 400
+runs for each of the comparisons for the second experiment.
 
-Table \ref{first-hypothesis-tests-training} summarizes the results obtained
-for each of the FISs in the training stage, as well as the t-value
-obtained when calculating a Student's t-test. The same structure is
-followed in Table \ref{first-hypothesis-tests-testing}, which shows the
-results obtained for each of the FISs in the testing stage.
+This first set of experiments used the same parameters
+described in Section \ref{experiments}, and even though the dimensions
+of the training and testing subsets of Mackey-Glass aren't the
+traditional ones, the IFIS still achieved very good results. These
+results can be found in Table \ref{first-hypothesis-tests-training}
+and Table \ref{first-hypothesis-tests-testing}.
 
@@
     \hline
-    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 & > 99.9\% \\
+    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 & $>$ 99.9\% \\
     \hline
-    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 & > 99.9\% \\
+    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 & $>$ 99.9\% \\
     \hline
-    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 & > 99.9\% \\
-    \hline
-  \end{tabular}
-\end{table}
-
-% con 400
-\begin{table}[!t]
-  \renewcommand{\arraystretch}{1.3}
-  \caption{Hypothesis Tests for the Training Stage, Second Experiment}
-  \label{second-hypothesis-tests-training}
-  \centering
-  \begin{tabular}{|c|c|c|c|c|c|}
-    \hline
-    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI\\
-    \hline
-    T1-IFIS & 76.22 & 16.90 & 400 & & \\
-    \hline
-    T1-FIS & 85.69 & 19.68 & 400 & -7.3013 & > 99.9\% \\
-    \hline
-    IT2-FIS (\(\mu\)) & 85.93 & 19.12 & 400 & -7.6102 & > 99.9\%\\
-    \hline
-    IT2-FIS (SD) & 99.78 & 19.04 & 400 & -18.508 & > 99.9\% \\
+    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 & $>$ 99.9\% \\
     \hline
@@
     \hline
-    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 & > 99.2\%\\
+    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 & $>$ 99.2\%\\
     \hline
-    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 & > 97.8\% \\
+    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 & $>$ 97.8\% \\
     \hline
-    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 & > 91.4\% \\
+    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 & $>$ 91.4\% \\
+    \hline
+  \end{tabular}
+\end{table}
+
+The second experiment follows exactly what is described in Section
+\ref{experiments}, i.e., in comparison to the first experiment, both the
+training dataset and testing dataset consist of 500 Mackey-Glass data
+points. As has been stated before, this is the traditional practice
+whet utilising the Mackey-Glass benchmark. Table
+\ref{second-hypothesis-tests-training} summarizes the results obtained
+for each of the FISs in the training stage, as well as the t-value
+obtained when calculating a Student's t-test. CI in this case stands
+for confidence interval. The same structure is followed in Table
+\ref{second-hypothesis-tests-testing}, which shows the
+results obtained for each of the FISs in the testing stage.
+
+% con 400
+\begin{table}[!t]
+  \renewcommand{\arraystretch}{1.3}
+  \caption{Hypothesis Tests for the Training Stage, Second Experiment}
+  \label{second-hypothesis-tests-training}
+  \centering
+  \begin{tabular}{|c|c|c|c|c|c|}
+    \hline
+    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI\\
+    \hline
+    T1-IFIS & 76.22 & 16.90 & 400 & & \\
+    \hline
+    T1-FIS & 85.69 & 19.68 & 400 & -7.3013 & $>$ 99.9\% \\
+    \hline
+    IT2-FIS (\(\mu\)) & 85.93 & 19.12 & 400 & -7.6102 & $>$ 99.9\%\\
+    \hline
+    IT2-FIS (SD) & 99.78 & 19.04 & 400 & -18.508 & $>$ 99.9\% \\
     \hline
@@
     \hline
-    T1-FIS & 152.26 & 126.47 & 400 & -1.6239 & > 89.4\% \\
+    T1-FIS & 152.26 & 126.47 & 400 & -1.6239 & $>$ 89.4\% \\
     \hline
-    IT2-FIS (\(\mu\)) & 154.37 & 119.92 & 400 & -1.9536 & > 94.8\% \\
+    IT2-FIS (\(\mu\)) & 154.37 & 119.92 & 400 & -1.9536 & $>$ 94.8\% \\
     \hline
-    IT2-FIS (SD) & 175.04 & 136.91 & 400 & -4.1492 & > 99.9\%\\
+    IT2-FIS (SD) & 175.04 & 136.91 & 400 & -4.1492 & $>$ 99.9\%\\
     \hline
@@
 and an IT2-FIS.
+
+In the training stage, every comparison achieved a confidence interval
+greater than 99.9\%. Although the stage of most interest is the
+testing stage, these results are still remarkable.
+
+The only comparison which did not achieve a confidence interval
+greater than 90\% was T1-IFIS vs. T1-FIS in the testing
+stage. Nevertheless, the comparisons against the IT2-FIS with
+uncertain mean and IT2-FIS with uncertain standard deviation achieved
+high confidence intervals in this stage.
 

### 2016-01-25 paper.tex
.eps extension in proposed-method-flow-chart
bigger figures
bigger figures cont.
All figures are pdfs now
removing comment
Corrections and results added

@@
 \usepackage[pdftex]{graphicx}
-\graphicspath{{./png/}{./eps/}}
-\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
+\graphicspath{{./pdf/}}
+\DeclareGraphicsExtensions{.pdf}
 
@@
 \begin{abstract}
-The concepts of intuitionistic membership, and intuitionistic center of
-area are proposed in this work, in order to propose a novel method for
-implementing an intuitionistic fuzzy inference system. The proposed
-method was implemented and compared against type-1 fuzzy inference
-systems and interval Type-2 fuzzy inference systems, with uncertain
+This work describes a method to construct type-1 intuitionistic fuzzy
+inference systems. This type of systems is able to handle more uncertainty than
+a type-1 fuzzy inference system and performs faster than a type-2
+fuzzy inference system. The concepts of intuitionistic membership, and
+intuitionistic center of area are proposed, in order to implement a
+system which is similar in design than the traditional fuzzy inference
+systems. The proposed method was implemented and compared against type-1 fuzzy inference
+systems and interval type-2 fuzzy inference systems, with uncertain
 means and uncertain standard deviations, by using the
 Mackey-Glass time series benchmark. A genetic algorithm was used to
-optimize the parameters of each of the methods being compared, and the
-results show that the intuitionistic fuzzy inference system performs
-better than the other methods.
+optimize the parameters of each of the methods being compared. This
+optimization ensures a fair comparison between each of the methods
+against the proposed method. The results show that the intuitionistic
+fuzzy inference system performs better than the other methods.
 \end{abstract}
@@
 
-Fuzzy sets were created as an extension to traditional sets, with
-uncertainty in mind, by L. A. Zadeh in 1965 \cite{zadeh1965fuzzy}. This uncertainty allows an
-element to be associated with a grade of membership that indicates
-how much that element belongs to a set, i.e., instead of
-belonging to a set (true, or 1), or not belonging (false, or 0),
-such element can belong in a grade from 0 to 1, and this is known as
-fuzzy logic \cite{klir1995fuzzy}.
-
-A derivation of logical conclusions can be performed by using premises
-that are assumed to be true, and this is known as inference, in
-traditional logic. The same
-technique can be extended to use fuzzy premises. In this case, all the
-premises hold a grade of truthiness, and a fuzzy conclusion is derived
-from the process. A popular method for performing such fuzzy inferences is a
-Mamdani Fuzzy Inference System (FIS) \cite{mamdani1975experiment},
-where the inputs are associated with fuzzy sets, and the outputs are
-fuzzy sets themselves, which can be converted to crisp numbers
-(this process is usually called \textit{defuzzification}). Other types of
-fuzzy inference engines exist, such as Takagi-Sugeno-Kang  (TSK)
-\cite{takagi1985fuzzy} and Tsukamoto \cite{tsukamoto1979approach}.
-
-Fuzzy sets were initially criticized because they were said to
-not be able to appropriately represent uncertainty. This problem was
-addressed by L. A. Zadeh in 1975 \cite{zadeh1975concept} by creating the
-concept of Type-2 Fuzzy Sets (T2-FS). This extension to type-1 fuzzy sets allowed the creation of
-type-2 fuzzy inference systems (T2-FIS) \cite{mendel2002type}, and those systems that used the
-traditional fuzzy sets are now called Type-1 Fuzzy Inference Systems
-(T1-FIS). T2-FIS have been proved to work better than T1-FIS in many
-situations, often problems that involve high levels of uncertainty, such as
-noisy data.
-
-Another extension to fuzzy sets, called Intuitionistic Fuzzy Sets
-(IFS), was proposed by K. T. Atanassov
-\cite{atanassov1986intuitionistic}. This extension adds the concepts
-of indeterminacy and non-membership to traditional fuzzy sets. In
-traditional fuzzy sets, the non-membership of an element is always the
-complement of the membership, but in an IFS, the non-membership can be
-represented by lower values (a deeper explanation of IFS is given in
-Section \ref{preliminaries}). Whenever the sum of the membership and
-the non-membership is less than 1, indeterminacy emerges, which
-represents the grade of uncertainty of an element of being or not
-being a member of a given set, with certain grade of membership. The
-concept of indeterminacy allows an expression such as ``This is
-somewhat tall, although I'm not very sure about my opinion.''
-
-The use of IFSs in a traditional FIS should enable the handling of more
-uncertainty, and one could prefer an Intuitionistic FIS (IFIS) to obtain
+The use of intuitionistic fuzzy sets (IFSs) in a traditional fuzzy
+inference system (FIS) should enable the handling of more
+uncertainty, and one could prefer an intuitionistic FIS (IFIS) to obtain
 better accuracies without sacrificing time performance, as
-inferences in a T2-FIS are very time consuming compared to a
-T1-FIS. This is a consequence of the complex type
+inferences in a type-2 FIS (T2-FIS) are very time consuming compared to a
+type-1 FIS (T1-FIS). This is a consequence of the complex type
 reducing procedure that is involved in the defuzzification stage in a
@@
 many works that require handling more uncertainty than a T1-FIS
-use a particular case of T2-FIS, the Interval T2-FIS (IT2-FIS)
-\cite{mendel2006interval}, which is faster than a general T2-FIS. A Type-1
-Intuitionistic FIS (T1-IFIS) should perform better than a T1-FIS in terms
+use a particular case of T2-FIS, the interval T2-FIS (IT2-FIS)
+\cite{mendel2006interval}, which is faster than a general T2-FIS (GT2-FIS). A type-1
+IFIS (T1-IFIS) should perform better than a T1-FIS in terms
 of accuracy (in problems involving data with high levels of
 uncertainty), and should be faster than a T2-FIS. Furthermore, IFSs
-can be implemented as part of a T2-FIS, giving as a result a T2-IFIS.
+can be implemented as part of a T2-FIS, giving as a result a type-2 IFIS.
 
@@
 
-A goal of this work is to propose a method to design a Mamdani IFIS that is
+Fuzzy sets were created as an extension to traditional sets, with
+uncertainty in mind, by L. A. Zadeh in 1965
+\cite{zadeh1965fuzzy}. This uncertainty allows an
+element to be associated with a grade of membership that indicates
+how much that element belongs to a set, i.e., instead of
+belonging to a set (true, or 1), or not belonging (false, or 0),
+such element can belong in a grade from 0 to 1, and this is known as
+fuzzy logic \cite{klir1995fuzzy}.
+
+A derivation of logical conclusions can be performed by using premises
+that are assumed to be true, and this is known as inference in
+traditional logic. The same technique can be extended to use fuzzy
+premises. In this case, all the
+premises hold a grade of truthiness, and a fuzzy conclusion is derived
+from the process. A popular method for performing such fuzzy inferences is a
+Mamdani FIS (FIS) \cite{mamdani1975experiment},
+where the inputs are associated with fuzzy sets, and the outputs are
+fuzzy sets themselves, which can be converted to crisp numbers
+(this process is usually called \textit{defuzzification}). Other types of
+fuzzy inference engines exist, such as Takagi-Sugeno-Kang  (TSK)
+\cite{takagi1985fuzzy} and Tsukamoto \cite{tsukamoto1979approach}.
+
+Fuzzy sets were initially criticized because they were said to
+not be able to appropriately represent uncertainty. This problem was
+addressed by L. A. Zadeh in 1975 \cite{zadeh1975concept} by creating the
+concept of type-2 fuzzy sets (T2-FS). This extension to type-1 fuzzy sets allowed the creation of
+T2-FISs \cite{mendel2002type}, and those systems that used the
+traditional fuzzy sets are now called type-1 fuzzy inference systems
+(T1-FIS). T2-FISs have been proved to work better than T1-FIS in many
+situations, often problems that involve high levels of uncertainty, such as
+noisy data \cite{mendel2001uncertain}.
+
+Another extension to fuzzy sets, called intuitionistic fuzzy sets, was
+proposed by K. T. Atanassov \cite{atanassov1986intuitionistic}. This
+extension adds the concepts of indeterminacy and non-membership to
+traditional fuzzy sets. In traditional fuzzy sets, the non-membership
+of an element is always the
+complement of the membership, but in an IFS, the non-membership can be
+represented by lower values (a deeper explanation of IFS is given in
+Section \ref{preliminaries}). Whenever the sum of the membership and
+the non-membership is less than 1, indeterminacy emerges, which
+represents the grade of uncertainty of an element of being or not
+being a member of a given set, with certain grade of membership. The
+concept of indeterminacy allows an expression such as ``This is
+somewhat tall, although I'm not very sure about my opinion'' to be
+represented in a FIS.
+
+The goal of this work is to propose a Mamdani IFIS that is
 similar in construction to the traditional Mamdani FIS. There are works
@@
 standard way of representing a fuzzy set. Some works use
-this way of representing an IFS (as in
-\cite{davarzani2013novel}). The proposal in this paper is to use the
+this way of representing an IFS (as in \cite{davarzani2013novel}). The
+proposal in this paper is to use the
 same convenient membership functions usually found in the design of
@@
 The method, for now, consists on the procedures and elements
-necessary to construct a basic Intuitionistic Fuzzy Inference System
-(IFIS). %(Mario)Por que basic?
-%% (A): Basic porque no añado que puedas poner OR en las reglas, no
-%% pongo otros métodos de defuzzificación, no pongo más funciones de
-%% membresía (triangulares, etc.). Explicaré eso (y)
-%(Mario)Tal vez enumerarlas? cuales procedures son?
-%% (A): Los procedures son los que están en el diagramita, y las
-%% explico abajo. Aun así las enumero?
+necessary to construct a basic IFIS, as this system can only handle
+Gaussian membership functions, and simple rules without AND or OR operators.
 An implementation was completed in order to make comparisons against
-classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
-Type-2 and General Type-2 FIS, and prove that
+traditional FISs, such as T1-FISs, IT2-FISs, and GT2-FIS, and prove that
 the design was viable and able to contribute to better results than
-the classic FISs.
+the traditional FISs.
 %(Mario)Es el proposito del diseño comparar? Creo que puedes decir mejor algo como:
@@
 
-In many works, intuitionistic fuzzy sets (IFSs) are constructed manualy,
+In many works, IFSs are constructed manually,
 by interviewing experts who assign memberships and
-non-memberships to each of the values of a set (such as in %to each of the members of a set?
+non-memberships to each of the elements of a set (such as in %to each of the members of a set?
 \cite{davarzani2013novel}). This work proposes a convenient way of
@@
 fuzzy interpretation. An example of an IFS is depicted in
-Figure \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
+Figure \ref{fs-as-ifs}. This IFS represents a traditional fuzzy set, as it
 satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
@@
   \centering
-  \includegraphics[width=2.5in]{fs-as-ifs}
-  \caption{Classic Fuzzy Set Represented as an Intuitionistic Fuzzy Set}
+  \includegraphics[width=3.0in]{fs-as-ifs}
+  \caption{Traditional Fuzzy Set Represented as an Intuitionistic Fuzzy Set}
   \label{fs-as-ifs}
@@
   \centering
-  \includegraphics[width=2.5in]{ifs}
+  \includegraphics[width=3.0in]{ifs}
   \caption{An Example of an Intuitionistic Fuzzy Set - Same Mean and SD}
@@
   \centering
-  \includegraphics[width=2.5in]{ifs-diff-mu-sd}
+  \includegraphics[width=3.0in]{ifs-diff-mu-sd}
   \caption{An Example of an Intuitionistic Fuzzy Set - Different Mean
@@
 
-The first step of the inference process in a classic FIS (a flow chart
+The first step of the inference process in a traditional FIS (a flow chart
 for the process in an IFIS is given in Figure \ref{flow-chart}) is to
@@
 %% otras partes, tengo que cambiarlo.
-MFs. This is straightforward in a classic FIS, as the
+MFs. This is straightforward in a traditional FIS, as the
 membership to each input is already established in the membership
@@
 which is described in (\ref{imembership}), and receives the name of
-$i\mu$ (intuitionistic membership). %(Mario)Creo que este podría ser
+intuitionistic membership and is represented as $i\mu$. %(Mario)Creo que este podría ser
                                 %el titulo
@@
   \centering
-  \includegraphics[width=2.5in]{if-membership}
+  \includegraphics[width=3.0in]{if-membership}
   \caption{Comparison of $\mu(x)$ Against $i\mu(x)$}
@@
   \centering
-  \includegraphics[width=2.5in]{if-membership-drastic}
+  \includegraphics[width=3.0in]{if-membership-drastic}
   \caption{Comparison of $\mu(x)$ Against $i\mu(x)$ With More Indeterminism}
@@
 
-The next step in the inference process is to perform an $\alpha$-cut % (Mario)
-La del FIS? aclaralo on the associated consequents to the antecedents that are
-activated by the inputs. In a classic FIS, this process is straightforward, as
+The next step in the inference process of a FIS is to perform an $\alpha$-cut % (Mario) La del FIS? aclaralo
+on the associated consequents to the antecedents that are
+activated by the inputs. In a traditional FIS, this process is straightforward, as
 the memeberships in a fuzzy set representing a consequent are ``cut'' by
@@
   \centering
-  \includegraphics[width=2.5in]{alpha-cut}
+  \includegraphics[width=3.0in]{alpha-cut}
   \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
@@
   \centering
-  \includegraphics[width=2.5in]{ifs-union}
+  \includegraphics[width=3.0in]{ifs-union}
   \caption{Union of Three $\alpha$-cut Intuitionistic Fuzzy Sets}
@@
 % Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
-fuzzy set, but the most frequently found in the literature is the
-Center of Area (CoA), or simply centroid. One can obtain the centroid
-of a classic fuzzy set A by using (\ref{center-of-area}). For an
+fuzzy set in a Mamdani FIS, but the most frequently found in the literature is the
+center of area (CoA) or centroid. One can obtain the centroid
+of a traditional fuzzy set A by using (\ref{center-of-area}). For an
 IFS, one can use the concept of intuitionistic membership ($i\mu$) and
@@
   \centering
-  \includegraphics[width=2.5in]{if-coa-vs-coa}
+  \includegraphics[width=3.0in]{if-coa-vs-coa}
   \caption{Comparison of $CoA_{A_{i}}$ Against $iCoA_{A_{i}}$}
@@
 proposed method is viable for performing inference using
-intuitionistic fuzzy sets instead of classic fuzzy sets, i.e., that
+intuitionistic fuzzy sets instead of traditional fuzzy sets, i.e., that
 the concepts of intuitionistic membership ($i\mu$) and intuitionistic
@@
 demonstrate this claim, this work presents a series of experiments
-where the proposed method is compared against Type-1 Fuzzy Inference
-Systems (T1-FISs) and Interval Type-2 Fuzzy Inference Systems
-(T2-FISs) with uncertain mean and uncertain standard deviation.
+where the proposed method is compared against T1-FISs and IT2-FISs
+with uncertain mean and uncertain standard deviation.
 
-The initial (and ambitious) hypothesis is that a Type-1 Intuitionistic Fuzzy System (T1-IFIS)
+The initial (and ambitious) hypothesis is that a T1-IFIS
 should perform better than a T1-FIS, as it can handle both uncertainty
@@
 A total of 400 runs were performed for every FIS. The decision for
-such a high number of runs was because of trial and error. Initially,
+that particular number of runs was because of trial and error. Initially,
 the IFIS was being tested with a subset of the Mackey-Glass time
@@
 of area ($iCoA$), proposed in Section \ref{proposed-method} allows the
-creation of a T1-IFIS that can perform better than a classic T1-FIS
+creation of a T1-IFIS that can perform better than a traditional T1-FIS
 and an IT2-FIS.
@@
 benchmarks, other than the Mackey-Glass time series. Also, this work
-should inspire the creation of Type-2 Intuitionistic Fuzzy Inference
-Systems (both the interval and general types).
+should inspire the creation of T2-IFIS (both the interval and general types).
 
